### 2018-07-04 paper/paper.tex
add paper scaffolding

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jonas Beyer \and
Philipp Otto\and
S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut für Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}

% Establish common ground with reader Worth readers time? Give some results

% Write it once at the start, then rewrite at the end
% use it to guide paper

% Important -> this structure will be expected

% Context (Topic / Terminology)
% Problem & Relevance (Problem - Costs / Current state - Gain)
% Related Work (Existing solutions / Shortcomings)
% Goals / Claims (Contribution, Sketch Results)
% Paper structure (The remainder of this paper is structured as follows ...)

What is BPMN?
What is Blockchain?
What problems are there with BPMN that can be solved with Blockchain?
What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
What is our general Idea?
What are our results? (briefly)

\section{Related Work}

summarize untrusted paper
summarize Caterpillar
acknowledge their Work
display the shortcomings

maybe also include Blockchain here?

\section{Solution approach}

basic understanding/ intuition
-> make orchestration possible

use one contuous example

visualizations !!

\section{Architecture}

\section{Evaluation}

\section{Conclusions}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references}

\end{document}

### 2018-07-04 paper/sample/samplepaper.tex
add paper scaffolding

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.
% ~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2018-07-04 paper/paper.tex
add figures to paper

@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+Blockchain technology enables untrusting parties to have trusted communication. We use this to implement a conversion of BPM choreographies to smart contracts on the Ethereum Blockchain.
 
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{fig/system_diagram.eps}
+\caption{The architecture of our design.} \label{fig1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig/initialization.eps}
+\caption{An initialization process.} \label{fig2}
+\end{figure}
+
 \section{Evaluation}

### 2018-07-09 paper/paper.tex
More paper scaffolding
Add blockchain part

@@
 \institute{
-Hasso-Plattner-Institut für Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
+Hasso-Plattner-Institut f\"ur Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
 \email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
@@
 
+\section{Preliminary}
+
+\subsection{Orchestractions and Choreographies}
+
+\subsection{Blockchain}
+A blockchain is a distributed ledger that allows users to find a concensus in decentralized applications.
+It works by splitting information into blocks that are connected as a linked list. 
+%TODO proof of work is only one possibility
+%TODO explain more in depth?
+Each block has to be signed in a way that is mathematically hard to calculate, but easy to verify.
+Therefore users can verify if their local blockchain is valid.
+If the same block is signed at the same time, a fork of the blockchain can happen, i.e. two versions of the same blockchain exist at the same time.
+A concensus is reached by propagating the longest blockchain within the network until it is accepted by all parties of the network.
+
+Blockchain technology is used in cryptocurrencies, most notably Bitcoin.
+The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
+Ethereum is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
+
+%TODO reference Bitcoin and ethereum paper
+
 \section{Related Work}
@@
 
+\subsection{Contract Structure}
+
+\subsection{Authorization}
+
+\subsection{Decentralization}
+% Decentralized contracts vs. central monitor
+% Engine on chain vs. message channel
+
 \section{Architecture}
+
+\subsection{System overview}
+
+\subsection{Per company setup}
+
+\subsection{Interaction setup}
+
+\subsection{Sending messages}
 
@@
 
+\section{Implementation}
+
+\subsection{Contracts}
+
+\subsection{eth\_admin}
+
+\subsection{armadillo}
+
 \section{Evaluation}
+%Gas cost
+%Time for one instance
+%Setup difficulty
+%Security
 
-\section{Conclusions}
+%Mention problem of giving and removing right to change access rights
+%But in the end one instance has to a be superadmin in the contract, if it is leaked there is a problem
+
+\section{Conclusion}
 

### 2018-07-09 paper/paper.tex
Fix merge

@@
 %
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
 %
@@
 \institute{
-Hasso-Plattner-Institut f\"ur Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
+Hasso-Plattner-Institut, Potsdam, Germany\\
 \email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
@@
 \begin{abstract}
-Blockchain technology enables untrusting parties to have trusted communication. We use this to implement a conversion of BPM choreographies to smart contracts on the Ethereum Blockchain.
+Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
+Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
+This allows for consensus in communication between otherwise untrusting parties.
+In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
+We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Blockchain \and Business Processes \and Ethereum \and Choreography \and Smart Contract \and BPMN}
 \end{abstract}
@@
 
-What is BPMN?
-What is Blockchain?
-What problems are there with BPMN that can be solved with Blockchain?
-What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
-What is our general Idea?
-What are our results? (briefly)
+% What is BPMN?
+The Business Process Model Notation (BPMN) enables detailed documentation of business processes.
+This is used to realize complex inter-business processes which involve vast communication structures.
+One common problem is that within these processes the parties have to trust each other.
+% What is Blockchain?
+
+With the increasing spread of Blockchain technology, this problem could be rectified.
+A Blockchain is a decentralized information-storage network.
+Information is stored in blocks, which are chained together via cryptograhic means.
+This means, that many participants can agree on a common public state of information without trusting each other.
+This technology is commonly used to realize virtual currencies, also called cryptocurrencies.
+Ethereum is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
+Smart contracts are small programs, which are ran by the Blockchain network. They have very limited processing power, but they enable the execution of code which has a commonly known state.
+
+%What problems are there with BPMN that can be solved with Blockchain?
+The problem of needing to trust each other when collaborating in a business process can be addressed by applying the benefits of blockchain technology.
+The Blockchain be used in several ways to facilitate trusted communication between untrusted parties.
+
+% What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
+Current approaches aim to convert the functionality of traditional BPMN Engines to smart contracts on the Ethereum Blockchain.
+
+Caterpillar~\cite{lopez2017caterpillar} features the implementation of most common BPMN elements.
+It enables the transformation of BPMN Models to smart contracts, which can be deployed and executed on the Blockchain.
+
+Weber et al.~\cite{weber2016untrusted} realize Orchestrations on the Blockchain.
+
+%What is our general Idea?
+We want to expand on the work of Weber et al.
+and implement true choreographies.
+In their current approach they are using one central smart contract called a mediator / monitor which manages the Orchestration state.
+We will have a set of smart contracts for every party, which will then communicate with each other to realize the choreography.
+%What are our results? (briefly)
 

### 2018-07-09 paper/paper.tex
More work on smart contract text

@@
 
-Blockchain technology is used in cryptocurrencies, most notably Bitcoin.
+%TODO reference original blockchain paper
+Blockchain technology is used in cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
 The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
-Ethereum is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
-
-%TODO reference Bitcoin and ethereum paper
+Ethereum \cite{wood2014ethereum} is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
+Smart contracts are Turing complete code artifacts, that can be deployed on the blockchain and have an interface that is callable by users. 
+They can receive and send money, store information locally and emit events on the blockchain ledger.
+When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
+Contracts deplete gas for each operation and return excess gas back to the user.
+This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
 

### 2018-07-09 paper/paper.tex
Preliminary intro
Start related work

@@
 \section{Preliminary}
+In the following section we present concepts and technologies that are related to our concept.
 
-\subsection{Orchestractions and Choreographies}
+\subsection{Orchestrations and Choreographies}
+A work by Weber et.
+al \citep{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
+They use a smart contract that all parties of a business process communicate with.
 
@@
 
-\section{Related Work}
-
-summarize untrusted paper
-summarize Caterpillar
-acknowledge their Work
-display the shortcomings
-
-maybe also include Blockchain here?
+\subsection{Prior Work on Business Processes on the Blockchain}
+%summarize untrusted paper
+%summarize Caterpillar
+%acknowledge their Work
+%display the shortcomings
 

### 2018-07-09 paper/paper.tex
Add notes for related work section

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
 \documentclass[runningheads]{llncs}
-%
+
 \usepackage{graphicx}
@@
 %
-\author{Jonas Beyer \and
-Philipp Otto\and
-S\"oren Tietb\"ohl}
+\author{Jonas Beyer \and Philipp Otto \and S\"oren Tietb\"ohl}
 %
@@
 Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
-This allows for consensus in communication between otherwise untrusting parties.
+As a result, it is possible to form consensus in the communication between otherwise untrusting parties.
 In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
@@
 
-\keywords{Blockchain \and Business Processes \and Ethereum \and Choreography \and Smart Contract \and BPMN}
+\keywords{Business Processes \and BPMN \and Choreographies \and Blockchain \and Ethereum \and Smart Contracts}
 \end{abstract}
@@
 \subsection{Orchestrations and Choreographies}
-A work by Weber et.
-al \citep{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
+A work by Weber et al. \cite{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
 They use a smart contract that all parties of a business process communicate with.
@@
 %summarize untrusted paper
+In \cite{weber2016untrusted}, a first approach of monitoring business process interactions on the blockchain was presented.
+Using a smart contract as a central \it{monitor} or \it{mediator} of the communication, a form of inter-process orchestration is implemented.
+
+we build on:
+factories \& instances
+registering users to roles
+triggers
+the model they used (originally from Fdhila et al)
+
+we don\'t:
+do bpmn solidity translation
+use one central contract instance
+
 %summarize Caterpillar
-%acknowledge their Work
-%display the shortcomings
+\cite{lopez2017caterpillar} presents an open-source implementation of an Ethereum-based process engine.
+
+describes components and architecture of engine
+automatic bpmn solidity translation
+no choreographies / lanes supported, all tasks / transitions are managed on-chain through process contract
 

### 2018-07-09 paper/paper.tex
Related work

--- 2018-07-09 paper/paper.tex
@@
 \subsection{Orchestrations and Choreographies}
-A work by Weber et.
-al \citep{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
-They use a smart contract that all parties of a business process communicate with.
 
@@
 This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
+%TODO short text on the paper which shows smart contract examples
 
@@
 %display the shortcomings
+A work by Weber et. al \cite{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
+They use a smart contract that all parties of a business process communicate with.
+They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
 

### 2018-07-10 paper/paper.tex
More notes, more gitignore

@@
 %TODO short text on the paper which shows smart contract examples
+%TODO short text on solidity
 
 \subsection{Prior Work on Business Processes on the Blockchain}
-%summarize untrusted paper
+In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
+Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
+They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
+They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
+In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
+%TODO highlight lack of access right explanation and problem of central contract?
+
+%we build on:
+%factories \& instances
+%registering users to roles
+%triggers
+%the model they used (originally from Fdhila et al)
+
+%we don\'t:
+%do bpmn solidity translation
+%use one central contract instance
+
 %summarize Caterpillar
@@
 %display the shortcomings
-A work by Weber et. al \cite{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
-They use a smart contract that all parties of a business process communicate with.
-They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
+\cite{lopez2017caterpillar} presents an open-source implementation of an Ethereum-based Business Process Management System.
+It implements BPMN-to-Solidity compilation and thereby tracks the state of process executions on the blockchain.
+Processes can be started and executed via a user interface, which calls the generated Solidity code in the background.
+
+%describes components and architecture of engine
+%automatic bpmn solidity translation
+%no choreographies / lanes supported, all tasks / transitions are managed on-chain through process %contract
 

### 2018-07-11 paper/paper.tex
rearrange and add more figures

@@
 
+factory (maps to process)
+creates instance (maps to process instance)
+also access contract for user rights management
+
 \subsection{Authorization}
+
+access contract API
 
@@
 
+Figure~\ref{fig:system_diagram} shows the architecture of our design.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=200px]{fig/system_diagram.eps}
+    \end{center}
+    \caption{The architecture of our design.} \label{fig:system_diagram}
+\end{figure}
+
 \subsection{Per company setup}
 
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=200px]{fig/initialization.eps}
+    \end{center}
+    \caption{An initialization process.} \label{fig:initialization}
+\end{figure}
+
 \subsection{Interaction setup}
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=200px]{fig/instance_creation.eps}
+    \end{center}
+    \caption{An initialization process.} \label{fig:instance_creation}
+\end{figure}
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{fig/system_diagram.eps}
-\caption{The architecture of our design.} \label{fig1}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig/initialization.eps}
-\caption{An initialization process.} \label{fig2}
+    \begin{center}
+        \includegraphics[width=200px]{fig/event_sending.eps}
+    \end{center}
+    \caption{An initialization process.} \label{fig:event_sending}
 \end{figure}
@@
 \subsection{Contracts}
+\cite{xu2018pattern}
+
+factory
+instance
+
+\subsubsection{Access Contract}
+
+we chose mapping approach
+other approaches part of further work, e.g. token based
 
 \subsection{eth\_admin}
+
+node-js command line tool using vorpal
+commands trigger blockchain calls using web3
 

### 2018-07-18 paper/paper.tex
Start with implementation section

--- 2018-07-10 paper/paper.tex
@@
 \usepackage{graphicx}
+\usepackage{listings}
 % Used for displaying a sample figure. If possible, figure files should
@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+\input{solidity-highlighting.tex}
 
@@
 
+Given the architecture, we will now discuss the implementation of a) the contracts used in the system, and b) the tools for interacting with the system.
+
 \subsection{Contracts}
 
+For taking part in the process collaboration, each company needs to deploy a factory contract that contains the contract definition of the company's instance contract.
+This closely follows the factory contract pattern used in \cite{weber2016untrusted}, and described as Pattern 14 in \cite{xu2018pattern}.
+
+- Split between choreography intiator and other participants
+- has following interface:
+  - constructor, passing the address of the access contract (needs to deployed first, details in next section)
+  - setters for dependent factories
+  - createInstance()
+  - getAccessAddress()
+  - isInstance(id, address)
+- has following internal impl
+  - guard instance creation until all dependent factories are set
+  -> hold list of addresses of dependent factories
+  - hold address of access contract
+  - hold mapping from uuid -> address, identifying its own instances for a given choreography id
+  - if initiator: generate uuid on createInstance
+
+The factory contract source code also contains the public interfaces of
+  - the access contract (same for every participant)
+  - remote factory contracts (if receiving messages from remote, for verification)
+  - remote instance contracts (if sending messages to remote instance)
+as well as the complete definition of the instance contract source code.
+
+The instance contract provides the following interface
+  - a constructor where the local access contract, the choreography id and all dependency addresses can be passed
+  - a function for each sending action (task or event), called from process engine
+  - a function for each receiving action (task or event), called from other instance contracts
+and the following internal impl
+  - hold the choreography id
+  - hold the addresses of its own factory (for selfdestruction) and its own access contract (for local verification)
+  - hold the addresses of remote factory and access contract (again, if receiving messages from remote)
+  - hold the addresses of remote instance contract (again, if sending messages)
+  - add guards to each sending action to verify the local sender
+  - add guards to each receiving action to verify the remote sender
+  - implement events and emit them to the blockchain on receive action, that can be watched from external triggers
+  - call remote receive functions on local send action
+  - selfdestruct on the last send or receive action of the instance
+
+Guards = access checks (Pattern 13)
+
+See appendix for example % TODO
+
+\subsubsection{Access Contract}
+
+Each company deploys an access contract that holds information about the roles and permissions of the company's employees.
+Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from \cite{xu2018pattern}.
+It allows decoupling the roles and permissions from the actual contract instances, allowing for a simple modification at runtime.
+Access contracts can be deployed per process, or even once per company as a single source of truth for all processes.
+
+To allow the administration of user permissions, access contracts provide the following interface:
+\begin{itemize}
+  \item 
+    \texttt{assignRoleToUser(userAddress, role)}
+  \item
+    \texttt{removeRoleFromUser(userAddress, role)}
+  \item
+    \texttt{assignTaskToRole(task, role)}
+  \item
+    \texttt{removeTaskFromRole(task, role)}
+\end{itemize}
+The access to these functions should be guarded, allowing only a specific administrator address to call them.
+
+Verifying a users permission to execute a certain task can be achieved by calling \texttt{isAuthorized(userAddress, task)}.
+\newline
+
+Given this interface, there are multiple possible implementation approaches for access contracts.
+As it was our main focus to develop a running prototype, and not to provide an optimized, production-ready system, we decided on a simple mapping-based implementation:
+\begin{lstlisting}[
+  caption=Mappings in our access contract implementation,
+  language=Solidity,
+  basicstyle=\small
+]
+pragma solidity ^0.4.23;
+
+contract Access {
+    mapping(string => string) taskToRole;
+    mapping(string => uint) roleToIndex;
+    mapping(address => uint) addressToAccessBitmask;
+    ...
+}
+\end{lstlisting}
+The first mapping stores the tasks that can be executed by a specific role (cf. pools and lanes, and their contained tasks, in BPMN diagrams).
+The second mapping assigns each role an index in the access bitmask, i.e., if the bit at the given index is set, the user holds the corresponding role.
+The third mapping assigns such an access bitmask to each user.
+
+Storing large amounts data on the blockchain is expensive by design.
+As the mappings grow in size with each user, role and task that is part of some process in the company, our implementation is probably not suited for real-world application.
+Finding optimized, less costly (both in computation cost and storage cost) approaches is part of future work.
+One other approach we thought of is based on Pattern 5 of \cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify one's role.
+
 \subsection{eth\_admin}
+
+node-js command line tool using vorpal
+commands trigger blockchain calls using web3
 
@@
 
+\section{Appendix}
+% TODO highlight different parts as described in section Implementation? or remove?
+\begin{lstlisting}[
+  caption=Example source code of the Bulk Buyer's factory contract,
+  language=Solidity,
+  basicstyle=\small,
+  xleftmargin=-3cm,
+  xrightmargin=-3cm]
+pragma solidity ^0.4.24;
+
+contract Manufacturer {
+    function receiveOrder(address) public;
+    function setBulkBuyer(address) public;
+}
+
+contract ManufacturerFactory {
+    function createInstance(uint) public returns(address);
+    function getAccessAddress() public returns(address);
+    function isInstance(uint, address) public view returns(bool);
+}
+
+contract Access {
+    function isAuthorized(address, string) public returns(bool);
+}
+
+contract BulkBuyer {
+    event ProductReceived();
+    event StartOfProductionReceived();
+    event Selfdestructed();
+
+    address _factory;
+    Access _localAccess;
+    uint _id;
+
+    ManufacturerFactory _manufacturerFactory;
+    Access _manufacturerAccess;
+    Manufacturer _manufacturer;
+
+    modifier manufacturerAuthorized(address sender, string taskName) {
+        require(_manufacturerFactory.isInstance(_id, msg.sender));
+        require(_manufacturerAccess.isAuthorized(sender, taskName));
+        _;
+    }
+
+    modifier localAuthorized(string taskName) {
+        require(_localAccess.isAuthorized(msg.sender, taskName));
+        _;
+    }
+
+    constructor(
+        address localAccess,
+        uint counter,
+        address manufacturerFactory, address manufacturerAccess, address manufacturerInstance
+    ) public {
+        _factory = msg.sender;
+        _localAccess = Access(localAccess);
+        _id = counter;
+
+        _manufacturerFactory = ManufacturerFactory(manufacturerFactory);
+        _manufacturerAccess = Access(manufacturerAccess);
+        _manufacturer = Manufacturer(manufacturerInstance);
+    }
+
+    function placeOrder() public localAuthorized("receiveOrder") {
+        _manufacturer.receiveOrder(msg.sender);
+    }
+
+    function receiveStartOfProduction(address sender) 
+      public manufacturerAuthorized(sender, "receiveStartOfProduction")
+    {
+        emit StartOfProductionReceived();
+    }
+
+    function receiveProduct(address sender) 
+      public manufacturerAuthorized(sender, "receiveProduct")
+    {
+        emit ProductReceived();
+        emit Selfdestructed();
+        selfdestruct(_factory);
+    }
+}
+
+contract BulkBuyerFactory {
+    event BulkBuyerInstanceCreated(address instanceAddress);
+
+    address _accessAddress;
+    uint _counter;
+
+    address _manufacturerAddress = address(0);
+
+    mapping(uint => address) _instances;
+
+    modifier initialized {
+        require(_manufacturerAddress != address(0));
+        _;
+    }
+
+    constructor(address accessAddress) public {
+        _accessAddress = accessAddress;
+        _counter = 0;
+    }
+
+    function setManufacturer(address manufacturerAddress) public {
+        _manufacturerAddress = manufacturerAddress;
+    }
+
+    function createInstance() public initialized returns(address) {
+        _counter = _counter + 1;
+
+        ManufacturerFactory manufacturerFactory = ManufacturerFactory(_manufacturerAddress);
+        address manufacturerAccess = manufacturerFactory.getAccessAddress();
+        address manufacturerInstance = manufacturerFactory.createInstance(_counter);
+
+        BulkBuyer b = new BulkBuyer(
+            _accessAddress,
+            _counter,
+            manufacturerFactory, manufacturerAccess, manufacturerInstance
+        );
+        _instances[_counter] = address(b);
+        emit BulkBuyerInstanceCreated(b);
+        return b;        
+    }
+
+    function getAccessAddress() public view returns(address) {
+        return _accessAddress;
+    }
+
+    function isInstance(uint id, address instanceAddress) public view returns(bool) {
+        return _instances[id] == instanceAddress;
+    }
+}
+\end{lstlisting}
+
 %

### 2018-07-18 paper/paper.tex
Work on solution approach

@@
 \section{Solution approach}
+We propose a system design, that allows choreographies to be executed publicly on the blockchain.
+In order to achieve this, every organization to provides an interface for their public process using smart contracts.
+We assume that all participating organizations use a process engine to execute their private processes.
+When a throw event is triggered within a process engine, a \emph{throw event function} is called on a smart contract and the corresponding \emph{catch event function} is called on the smart contract of the organization responsible for catching the event.
+Thus, the public processes of all organizations are recorded on the blockchain.
 
-basic understanding/ intuition
--> make orchestration possible
+%TODO reference "trigger" from Untrusted paper
+Each organization uses a \emph{trigger} that continuously listens to catch events.
+If a catch event is observed, this information is relayed to the process engine to handle the event.
+The usage of the blockchain to monitor the choreography is encapsulated in the process engine and is therefore hidden from the users.
 
-use one contuous example
+%basic understanding/ intuition
+%-> make orchestration possible
 
-visualizations !!
+%use one contuous example
+
+%visualizations !!
 
 \subsection{Contract Structure}
+To realize the system, we use three kinds of smart contracts.
+Firstly, each organization uses one \emph{instance contract} per process instance.
+It represents the public process of the organization for the corresponding process.
+It is called during the process execution when a catch or throw event is reached in the process instance.
+When this happens, it emits an event on the blockchain to document this fact.
 
-factory (maps to process)
-creates instance (maps to process instance)
-also access contract for user rights management
+Secondly, each organization uses one \emph{factory contract} per process.
+It is responsible for creating instance contracts and saving a mapping from instance IDs to the corresponding contracts.
+
+Thirdly, each organization uses \emph{access contracts} to manage which users can trigger events on the instance contracts.
+Either, there is on access contract per process or access contracts are shared over multiple processes depending on the use case.
+
+%factory (maps to process)
+%creates instance (maps to process instance)
+%also access contract for user rights management
 
 \subsection{Authorization}
-
-access contract API
+In order to authorize users, the instance contract calls the access contract.
 

### 2018-07-18 paper/paper.tex
Reformat, small structure changes

@@
 
-Given the architecture, we will now discuss the implementation of a) the contracts used in the system, and b) the tools for interacting with the system.
+Given the architecture, we will now discuss the implementation of the contracts used in the system.
+Afterwards, we will shortly describe the tools we built for interacting with the system.
 
 \subsection{Contracts}
+
+\subsubsection{Process Contracts}
 
@@
 
-\subsection{eth\_admin}
+\subsection{Tools}
+
+\subsubsection{eth\_admin}
 
@@
 
-\subsection{armadillo}
+\subsubsection{armadillo}
 

### 2018-07-18 paper/paper.tex
Restructuring

@@
 \authorrunning{J. Beyer et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
 %
@@
 
+% Decentralized contracts vs. central monitor
+% Engine on chain vs. message channel
+
 %use one contuous example
@@
 %visualizations !!
+
+\subsection{System overview}
+
+\begin{figure}
+	\includegraphics[width=\textwidth]{fig/system_diagram.eps}
+	\caption{The architecture of our design.} \label{fig1}
+\end{figure}
 
@@
 
-\subsection{Authorization}
-In order to authorize users, the instance contract calls the access contract.
+\subsection{Per company setup}
 
-\subsection{Decentralization}
-% Decentralized contracts vs. central monitor
-% Engine on chain vs. message channel
-
-\section{Architecture}
-
-\subsection{System overview}
-
-\subsection{Per company setup}
+\begin{figure}
+	\includegraphics[width=\textwidth]{fig/initialization.eps}
+	\caption{An initialization process.} \label{fig2}
+\end{figure}
 
@@
 
-\begin{figure}
-	\includegraphics[width=\textwidth]{fig/system_diagram.eps}
-	\caption{The architecture of our design.} \label{fig1}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\textwidth]{fig/initialization.eps}
-	\caption{An initialization process.} \label{fig2}
-\end{figure}
+\subsection{Authorization}
+In order to authorize users, the instance contract calls the access contract.
 
@@
 
-See appendix for example % TODO
+See github repo for example % TODO
 
@@
 
+% future work: 
+% - access contract
+% - instantiation
+% - automatic generation -> template
 \section{Conclusion}
-
-\section{Appendix}
-% TODO highlight different parts as described in section Implementation? or remove?
-\begin{lstlisting}[
-  caption=Example source code of the Bulk Buyer's factory contract,
-  language=Solidity,
-  basicstyle=\small,
-  xleftmargin=-3cm,
-  xrightmargin=-3cm]
-pragma solidity ^0.4.24;
-
-contract Manufacturer {
-    function receiveOrder(address) public;
-    function setBulkBuyer(address) public;
-}
-
-contract ManufacturerFactory {
-    function createInstance(uint) public returns(address);
-    function getAccessAddress() public returns(address);
-    function isInstance(uint, address) public view returns(bool);
-}
-
-contract Access {
-    function isAuthorized(address, string) public returns(bool);
-}
-
-contract BulkBuyer {
-    event ProductReceived();
-    event StartOfProductionReceived();
-    event Selfdestructed();
-
-    address _factory;
-    Access _localAccess;
-    uint _id;
-
-    ManufacturerFactory _manufacturerFactory;
-    Access _manufacturerAccess;
-    Manufacturer _manufacturer;
-
-    modifier manufacturerAuthorized(address sender, string taskName) {
-        require(_manufacturerFactory.isInstance(_id, msg.sender));
-        require(_manufacturerAccess.isAuthorized(sender, taskName));
-        _;
-    }
-
-    modifier localAuthorized(string taskName) {
-        require(_localAccess.isAuthorized(msg.sender, taskName));
-        _;
-    }
-
-    constructor(
-        address localAccess,
-        uint counter,
-        address manufacturerFactory, address manufacturerAccess, address manufacturerInstance
-    ) public {
-        _factory = msg.sender;
-        _localAccess = Access(localAccess);
-        _id = counter;
-
-        _manufacturerFactory = ManufacturerFactory(manufacturerFactory);
-        _manufacturerAccess = Access(manufacturerAccess);
-        _manufacturer = Manufacturer(manufacturerInstance);
-    }
-
-    function placeOrder() public localAuthorized("receiveOrder") {
-        _manufacturer.receiveOrder(msg.sender);
-    }
-
-    function receiveStartOfProduction(address sender) 
-      public manufacturerAuthorized(sender, "receiveStartOfProduction")
-    {
-        emit StartOfProductionReceived();
-    }
-
-    function receiveProduct(address sender) 
-      public manufacturerAuthorized(sender, "receiveProduct")
-    {
-        emit ProductReceived();
-        emit Selfdestructed();
-        selfdestruct(_factory);
-    }
-}
-
-contract BulkBuyerFactory {
-    event BulkBuyerInstanceCreated(address instanceAddress);
-
-    address _accessAddress;
-    uint _counter;
-
-    address _manufacturerAddress = address(0);
-
-    mapping(uint => address) _instances;
-
-    modifier initialized {
-        require(_manufacturerAddress != address(0));
-        _;
-    }
-
-    constructor(address accessAddress) public {
-        _accessAddress = accessAddress;
-        _counter = 0;
-    }
-
-    function setManufacturer(address manufacturerAddress) public {
-        _manufacturerAddress = manufacturerAddress;
-    }
-
-    function createInstance() public initialized returns(address) {
-        _counter = _counter + 1;
-
-        ManufacturerFactory manufacturerFactory = ManufacturerFactory(_manufacturerAddress);
-        address manufacturerAccess = manufacturerFactory.getAccessAddress();
-        address manufacturerInstance = manufacturerFactory.createInstance(_counter);
-
-        BulkBuyer b = new BulkBuyer(
-            _accessAddress,
-            _counter,
-            manufacturerFactory, manufacturerAccess, manufacturerInstance
-        );
-        _instances[_counter] = address(b);
-        emit BulkBuyerInstanceCreated(b);
-        return b;        
-    }
-
-    function getAccessAddress() public view returns(address) {
-        return _accessAddress;
-    }
-
-    function isInstance(uint id, address instanceAddress) public view returns(bool) {
-        return _instances[id] == instanceAddress;
-    }
-}
-\end{lstlisting}
 

### 2018-07-18 paper/paper.tex
Work on Solution approach

@@
 We propose a system design, that allows choreographies to be executed publicly on the blockchain.
-In order to achieve this, every organization to provides an interface for their public process using smart contracts.
-We assume that all participating organizations use a process engine to execute their private processes.
-When a throw event is triggered within a process engine, a \emph{throw event function} is called on a smart contract and the corresponding \emph{catch event function} is called on the smart contract of the organization responsible for catching the event.
-Thus, the public processes of all organizations are recorded on the blockchain.
-
-%TODO reference "trigger" from Untrusted paper
-Each organization uses a \emph{trigger} that continuously listens to catch events.
-If a catch event is observed, this information is relayed to the process engine to handle the event.
-The usage of the blockchain to monitor the choreography is encapsulated in the process engine and is therefore hidden from the users.
+In the following section, we describe our approach and its architecture.
 
@@
 \subsection{System overview}
+\begin{figure}
+	\centering
+	\includegraphics[width=100mm]{fig/system_diagram.eps}
+	\caption{An architecture diagram showing the interactions within the system.} 			
+	\label{fig:system_diagram}
+\end{figure}
 
-\begin{figure}
-	\includegraphics[width=\textwidth]{fig/system_diagram.eps}
-	\caption{The architecture of our design.} \label{fig1}
-\end{figure}
+Every organization provides an interface of their public process in an \emph{instance contract}.
+Additionally, \emph{factory contracts} manage these instance contracts and \emph{access contracts} are used for rights management.
+The contract structure will be described in detail in the following sections.
+We assume that all participating organizations use a process engine to execute their private processes.
+When a throw event is triggered within a process engine, a \emph{throw event function} is called on an instance contract and the corresponding \emph{catch event function} is called on the instance contract of the organization responsible for catching the event.
+Thus, the public processes of all organizations are recorded on the blockchain.
+
+%TODO reference "trigger" from Untrusted paper
+Each organization uses a \emph{trigger} that continuously listens to catch events.
+If a catch event is observed, this information is relayed to the process engine to handle the event.
+The usage of the blockchain to monitor the choreography is encapsulated in the process engine and is therefore hidden from the users.
+
+The interaction of the components can be seen in Figure \ref{fig:system_diagram}.
 
@@
 
-%factory (maps to process)
-%creates instance (maps to process instance)
-%also access contract for user rights management
-
 \subsection{Per company setup}
-
 \begin{figure}
-	\includegraphics[width=\textwidth]{fig/initialization.eps}
-	\caption{An initialization process.} \label{fig2}
+	\centering
+	\includegraphics[width=70mm]{fig/initialization.eps}
+	\caption{A sequence diagram describing the initialization process for an organization.} 
+	\label{fig:initialization}
 \end{figure}
 
+%TODO add a step where other factory contracts are set
+Each organization needs to perform some setup before they can take part in a process execution.
+An access contract and a factory contract for a process need to be deployed it it has not been done yet.
+Additionally, the user-to-role and and task-to-role mappings have to be updated, to allow verification of users during the process execution.
+A diagram of this process can be seen in Figure \ref{fig:initialization}.
+
 \subsection{Interaction setup}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{fig/instance_creation.eps}
+	\caption{A sequence diagram describing the process of creating a new process instance.} 
+	\label{fig:instance_creation}
+\end{figure}
+
+In order to create a new process instance, the organization that initiates the instance by triggering the first throw event has to explicitly create an instance contract by calling the factory contract.
+To create an instance contract, the factory contract may need to initialize other instance contracts by calling other factory contracts.
+When all partner instance, factory and access contracts are known, the instance contract can be created and its address is returned to the user and an event is emitted to the blockchain.
+This process is visualized in Figure \ref{fig:instance_creation}.
+
+The recursive initialization ensures that all instance contracts that are part of the process instance will be created by one function call.
+%TODO add emit event in the diagram
+%TODO better formulation
+The organizations that did not start the instance creation can detect the new process instance by using their trigger to watch the factory contract.
 
 \subsection{Sending messages}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{fig/event_sending.eps}
+	\caption{A sequence diagram describing the process of sending a message to a collaboration partner.} 
+	\label{fig:event_sending}
+\end{figure}
 

### 2018-07-18 paper/paper.tex

@@
 
-\subsection{Authorization}
-In order to authorize users, the instance contract calls the access contract.
+%TODO correctly show that the address is passed instead of using msg.sender
+When a throw event is triggered in the process engine of organization $A$, the corresponding \emph{throw event function} is called on the instance contract of the collaboration partner $B$.
+In the instance contract of $A$ an authorization is performed by looking up the sender address in the access contract of $A$.
+If this check is successful, the \emph{catch event function} is called on the partner instance contract of $B$.
+In the instance contract of $B$ there is another authorization against the access contract of $A$.
+This ensures that both sides can be confident, that the throw event was triggered by an authorized person who belongs to organization $A$.
+If this check was also successful, an event is emitted to the blockchain.
+This will be detected by the trigger of $B$ and passed to the process engine.
+Thus, a message was sent from $A$ to $B$ via the blockchain and an audit trail was created.
+An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.
 

### 2018-07-18 paper/paper.tex
add some orchestration and choreography

@@
 \subsection{Orchestrations and Choreographies}
+
+When speaking about a Buisiness Process with multiple participants, there are generally two types of perspectives the Process Model can have: Orchestrations and Choreographies.
+Orchestrations view the Process from a central perspective, and contain only one main pool which the process is focused around. 
+They describe the internal process of an organization represented by the pool.
+External communication partners can be included as pools aswell, however their internal processes are not modeled.
+This gives the model a clear state and order in which it has to be executed.
+The main pool inhibits the role of a mediator or manager, dictating and guiding the execution.
+
+In a choreography, the participants are much more independent.
+There is no clear order or state, because the participants are acting and communicating independent of others.
+An orchestration includes all public processes of each pool, as well as the communication between the processes.
+
+One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the interpretation of orchestration and choreography.
+Weber et al. implement choreographies by means of a central mediator/monitor contract.
+Thus every step in the process is managed by this central contract.
+The contract also holds an internal state of the process.
+By our interpretation of the terms, this would not be a choreography but an orchestration.
+Therefore we wanted to implement a solution, which models each pool seperately as their own entity, including having their own contracts.
+Our goal is to decrease the amount trust needed between the communication partners.
+By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.
 

### 2018-07-19 paper/paper.tex
Add hyperref package, more implementation

--- 2018-07-18 paper/paper.tex
@@
 \usepackage{listings}
+\usepackage{hyperref}
 % Used for displaying a sample figure. If possible, figure files should
@@
 % to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 
+In the following, we will formally describe our contract implementations.
+The implemented contracts can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/tree/master/armadillo/resources}.
+% TODO repo ist noch private
+% TODO update if repository changes
+
 \subsubsection{Process Contracts}
 
-For taking part in the process collaboration, each company needs to deploy a factory contract that contains the contract definition of the company's instance contract.
+For taking part in the process collaboration, each company needs to deploy a factory contract that is responsible for creating instance contracts.
+To this end, the factory contract source code needs to contain the definition of the company's instance contract.
 This closely follows the factory contract pattern used in \cite{weber2016untrusted}, and described as Pattern 14 in \cite{xu2018pattern}.
 
-- Split between choreography intiator and other participants
-- has following interface:
-- constructor, passing the address of the access contract (needs to deployed first, details in next section)
-- setters for dependent factories
-- createInstance()
-- getAccessAddress()
-- isInstance(id, address)
-- has following internal impl
-- guard instance creation until all dependent factories are set
--> hold list of addresses of dependent factories
-- hold address of access contract
-- hold mapping from uuid -> address, identifying its own instances for a given choreography id
-- if initiator: generate uuid on createInstance
+In our implementation, a company's factory contract also knows the address of the company's access contract for convenience.
+Additionally, it stores the addresses of created instances, mapped by a \textit{choreography instance ID}, i.e., an ID that is shared between all choreography participants for each instance of the shared choreography.
+
+To allow interaction between companies via the blockchain, two participants need to exchange the addresses of their factory contracts when there is a direct interaction between them.
+
+A factory contract thus has the resulting interface:
+\begin{itemize}
+	\item A \texttt{constructor} where the address of the company's access contract is passed
+	\item Setter methods for the factory contract addresses of interaction partners
+	\item A \texttt{createInstance} function
+	\item A \texttt{getAccessAddress} function
+	\item A \texttt{isInstance} function, checking if a given address belongs to an instance created by this factory, for a given choreography instance ID % TODO rephrase?
+\end{itemize}
+
+Internally, there are a few implementation details worth mentioning.
+Regarding storage, private fields are necessary holding the factory contract addresses, the access contract address as well as the instance address mapping.
+To avoid communication errors at runtime, it should not be possible to call \texttt{createInstance} before all required factory addresses are set.
+Finally, there is one minor implementation difference depending on whether a participant is the \textit{choreography initiator} -- the participant to manually start the choreography instance by sending a request -- or instead is starting its instance as a response to another participant's request: % TODO arrgh bessere formulierung
+The initiator needs to generate the choreography instance ID inside of its \texttt{createInstance} function, and pass it to all its interaction partners.
+Every other participant needs to have a parameter for the ID in their \texttt{createInstance} function.
 

### 2018-07-19 paper/paper.tex
Shrink images a bit
Use monospace font for listings

@@
 \input{solidity-highlighting.tex}
+
+\lstset{basicstyle=\small\ttfamily}
 
@@
 	\centering
-	\includegraphics[width=100mm]{fig/system_diagram.eps}
+	\includegraphics[width=0.6\textwidth]{fig/system_diagram.eps}
 	\caption{An architecture diagram showing the interactions within the system.} 			
@@
 	\centering
-	\includegraphics[width=70mm]{fig/initialization.eps}
+	\includegraphics[width=0.45\textwidth]{fig/initialization.eps}
 	\caption{A sequence diagram describing the initialization process for an organization.} 
@@
   caption=Mappings in our access contract implementation,
-  language=Solidity,
-  basicstyle=\small
+  language=Solidity
 ]

### 2018-07-19 paper/paper.tex
Finish contracts section

@@
 
-The factory contract source code also contains the public interfaces of
-- the access contract (same for every participant)
-- remote factory contracts (if receiving messages from remote, for verification)
-- remote instance contracts (if sending messages to remote instance)
-as well as the complete definition of the instance contract source code.
+Communication between smart contracts happens in the form of function calls.
+To allow the factory and instance contracts to call functions on their interaction partner's contracts, the partner's function interface needs to be known, i.e., it needs to be declared in the factory contract source code.
+%- the access contract (same for every participant)
+%- remote factory contracts (if receiving messages from remote, for verification)
+%- remote instance contracts (if sending messages to remote instance)
 
-The instance contract provides the following interface
-- a constructor where the local access contract, the choreography id and all dependency addresses can be passed
-- a function for each sending action (task or event), called from process engine
-- a function for each receiving action (task or event), called from other instance contracts
-and the following internal impl
-- hold the choreography id
-- hold the addresses of its own factory (for selfdestruction) and its own access contract (for local verification)
-- hold the addresses of remote factory and access contract (again, if receiving messages from remote)
-- hold the addresses of remote instance contract (again, if sending messages)
-- add guards to each sending action to verify the local sender
-- add guards to each receiving action to verify the remote sender
-- implement events and emit them to the blockchain on receive action, that can be watched from external triggers
-- call remote receive functions on local send action
-- selfdestruct on the last send or receive action of the instance
+The instance contract definition is also part of the factory contract source code.
+The factory contract creates an instance by calling its constructor and passing all for the inter-process communication required addresses.
+Instance contracts provide functions for each sending action, i.e., send tasks or events in the company's process, which can be called by the process engine.
+For each receiving action (task or event), a function needs to be present that can be called from other instance contracts.
+When company $A$ triggers a sending function on their instance contract, it in turn calls a corresponding receive function on the instance contract of company $B$.
 
-Guards = access checks (Pattern 13)
+Instance contracts need to store:
+\begin{itemize}
+	\item The choreography instance ID for verifying incoming messages
+	\item The addresses of the factory and access contracts of partners for verifying incoming messages
+	\item The addresses of the instance contracts of partners for sending messages
+	\item The address of the company's own access contract, for verifying local function calls
+	\item The address of the company's own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
+\end{itemize}
 
-See github repo for example % TODO
+A few more implementation details are worth noting:
+Verification is implemented on sender-side and on receiver side.
+Each send function has a guard checking the caller in the company's own access contract.
+Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partner's access contract.
+Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in \cite{xu2018pattern}.
+
+Having achieved a traceable communication on the blockchain using contract function calls, we still want to access messages in off-chain applications, e.g., triggering process events in a process engine on message receive.
+To this end, smart contracts need to implement events that are omitted to the blockchain whenever a receive function is executed.
+Blockchain events can then be watched, and reacted upon, by off-chain components.
+
+In our current implementation, the end of a process instance is marked by the instance contract selfdestructing.
+At the end of the execution of the last send or receive function in the process, the solidity builtin \texttt{selfdestruct} is called.
+By passing the factory contract address, potential remaining funds are transferred to the factory contract.
 
@@
 \begin{itemize}
-	\item
-	      \texttt{assignRoleToUser(userAddress, role)}
-	\item
-	      \texttt{removeRoleFromUser(userAddress, role)}
-	\item
-	      \texttt{assignTaskToRole(task, role)}
-	\item
-	      \texttt{removeTaskFromRole(task, role)}
+	\item \texttt{assignRoleToUser(userAddress, role)}
+	\item \texttt{removeRoleFromUser(userAddress, role)}
+	\item \texttt{assignTaskToRole(task, role)}
+	\item \texttt{removeTaskFromRole(task, role)}
 \end{itemize}

### 2018-07-19 paper/paper.tex
Add description of eth admin and armadillo

@@
 Thirdly, each organization uses \emph{access contracts} to manage which users can trigger events on the instance contracts.
-Either, there is on access contract per process or access contracts are shared over multiple processes depending on the use case.
+Either there is one access contract per process or access contracts are shared over multiple processes depending on the use case.
 
@@
 
-\subsubsection{eth\_admin}
+In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
+The implementations can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
+% TODO repo ist noch private
+% TODO update if repository changes
+% TODO overfull hbox
 
-node-js command line tool using vorpal
-commands trigger blockchain calls using web3
+\subsubsection{Armadillo}
 
-\subsubsection{armadillo}
+As a way of joining process execution with our blockchain architecture, we developed a single page web application in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
+With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
+Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
+Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on tasks, which allowed us to use the viewer as a process engine mock.
+A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/blob/master/presentation/armadillo-screencast.mp4}.
+% TODO repo, hbox etc.
+
+\subsubsection{Eth\_Admin}
+
+We developed a small command line application for managing users and roles via the access contract.
+The application is written in JavaScript in the node.js framework\footnote{\url{https://nodejs.org/}}.
+Internally, calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
+We decide to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
+The README in our repository describes how to use the application.
 

### 2018-07-22 paper/paper.tex
Evaluation & Further Work

@@
 %
+% TODO casing of headlines (capital)
 \section{Introduction}
@@
 \section{Evaluation}
-%Gas cost
+
+When evaluating blockchain implementations, the underlying system comes with new aspects that need to be considered.
+First, computation and data storage on the blockchain needs to be paid for in \textit{transaction fees}.
+In Ethereum, the unit \textit{gas} was introduced as a way of having consistent fee pricing in spite of fluctuating Ether prices.
+
+We measured the gas used for each transaction that is executed by the Armadillo tool, and we summed up the gas usage for the different kinds of contracts in the companies in the following table:
+
+\begin{tabular}{l|l|l|l}
+	% TODO
+	a & b & c & d
+\end{tabular}
+
+Most of the transactions have proven to come with reasonable gas costs.
+However, the instantiation cost that is currently paid by the initiator appears to be problematic.
+As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \textit{gas limit}, the maximum amount of gas that can be spent per transaction.
+Even if that is not the case, a high gas cost is still a problem, since transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times.
+% TODO explain?
+
+Second, security is one of the main reasons to opt for blockchain systems.
+In our case, we put effort into making the message exchange secure by adding multiple steps of access verification using the access contracts.
+Access contracts themselves, however, only implement access verification by comparing the sender address with the address the contract was deployed with (the \textit{owner} address).
+As the owner can give and remove access rights freely, another layer of off-chain security might make sense here to restrict the owner account from unwanted access.
+
 %Time for one instance
 %Setup difficulty
-%Security
 
-%Mention problem of giving and removing right to change access rights
-%But in the end one instance has to a be superadmin in the contract, if it is leaked there is a problem
+\section{Future Work}
 
-% future work: 
-% - access contract
-% - instantiation
-% - automatic generation -> template
+We researched a system prototype for handling process choreographies on the blockchain.
+While we were able to execute an example choreography using our implementation, a few aspects are left for future work.
+
+\paragraph{Access Contract}
+
+As stated earlier, there possibly are better ways of implementing a role-based access control inside a smart contract.
+We decided for a simple mapping-based approach, which requires a relatively large amount of memory.
+Finding approaches that are more suited for blockchain architectures is one direction in which further research could go.
+
+\paragraph{Instantiation Costs}
+
+\paragraph{Contract Generation}
+
+\paragraph{Process Engine Integration}
+
 \section{Conclusion}

### 2018-07-23 paper/paper.tex
proof read, add more todos

@@
 \section{Introduction}
+% TODO: rewrite introduction
 
@@
 
+% TODO write more here
 Weber et al.~\cite{weber2016untrusted} realize Orchestrations on the Blockchain.
@@
 
+% TODO improve wording
 When speaking about a Buisiness Process with multiple participants, there are generally two types of perspectives the Process Model can have: Orchestrations and Choreographies.
@@
 Therefore we wanted to implement a solution, which models each pool seperately as their own entity, including having their own contracts.
-Our goal is to decrease the amount trust needed between the communication partners.
+Our goal is to decrease the amount of trust needed between the communication partners.
 By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.
+
+% TODO write about public and private processes
 
@@
 Each organization needs to perform some setup before they can take part in a process execution.
-An access contract and a factory contract for a process need to be deployed it it has not been done yet.
+An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
 Additionally, the user-to-role and and task-to-role mappings have to be updated, to allow verification of users during the process execution.
@@
 Having achieved a traceable communication on the blockchain using contract function calls, we still want to access messages in off-chain applications, e.g., triggering process events in a process engine on message receive.
-To this end, smart contracts need to implement events that are omitted to the blockchain whenever a receive function is executed.
+To this end, smart contracts need to implement events that are emitted to the blockchain whenever a receive function is executed.
 Blockchain events can then be watched, and reacted upon, by off-chain components.

### 2018-07-23 paper/paper.tex
more future work

@@
 
+During evaluation, we saw that the instantiation costs are very high, have a potential to hit the gas limit in larger choreographies and also have to be paid by the initiator.
+These problems need to be addressed before our solution is viable for production use.
+One possbile way to distribute the costs among the participants makes use of triggers on the factory contracts.
+Instead of creating all instance contracts transitively, the factory contract would have a method for accepting requests for instantiation.
+The process engine could then react to such a call via a trigger, and call the instantiation method.
+Then the other factory would have to be notified that the instantiation was successful.
+
 \paragraph{Contract Generation}
+
+Currently all contracts are written manually.
+Since the contracts all share the same patterns,  this is a prime candidate for automation.
+A possible implementation could use a rule-based approach for translating the choreography model, similar to \cite{lopez2017caterpillar}.
+This would then automatically generate Solidity code for the access and factory contracts.
 

### 2018-07-23 paper/paper.tex
Merge further work changes

@@
 Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
-Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on tasks, which allowed us to use the viewer as a process engine mock.
+Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \textit{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
 A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/blob/master/presentation/armadillo-screencast.mp4}.
@@
 
-\paragraph{Access Contract}
+\subsubsection{Instantiation Costs}
 
-As stated earlier, there possibly are better ways of implementing a role-based access control inside a smart contract.
-We decided for a simple mapping-based approach, which requires a relatively large amount of memory.
-Finding approaches that are more suited for blockchain architectures is one direction in which further research could go.
-
-\paragraph{Instantiation Costs}
+In the evaluation, we realized that the instantiation cost currently is too high for our system to be used in a productive environment.
+Further research thus could be invested into a more decentralized instantiation, where each participant pays for its own instance contract creation.
+One approach we discussed, but did not have the time to implement, would be to have the intiator emit a specific instance creation event that each other participant would listen to.
+Then, a trigger could be implemented, that calls the \texttt{createInstance} method as soon as the event is received.
 
@@
 
-\paragraph{Contract Generation}
+\subsubsection{Access Contract}
+
+As stated earlier, there possibly are better ways of implementing a role-based access control inside a smart contract.
+We decided for a simple mapping-based approach, which requires a relatively large amount of memory.
+Finding approaches that are more suited for blockchain architectures is one direction in which further research could go.
+
+\subsubsection{Process Contract Generation}
+
+Our contract implementations are the result of manual, iterative development.
+Having reached the final iteration, we realized that most of the implementation could probably be generated, i.e., from a choreography diagram (or at least from the participant's public processes).
+The next step would be to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments, e.g., depending on whether the participant is the initiator or not.
+Given such a template, one could work on a contract generation tool that takes a diagram as input and produces factory contract code.
 
@@
 
-\paragraph{Process Engine Integration}
+\subsubsection{Process Engine Integration}
+
+In related work \cite{lopez2017caterpillar}, process logic was executed on the blockchain.
+As we decided for a hybrid approach, using a process engine for execution and the Ethereum blockchain for traceable message passing, we implemented a mock process engine in our application.
+Now, it certainly makes sense to integrate the system with a productive process engine implementation, e.g., the Camunda BPMN Workflow Engine\footnote{\url{https://camunda.com/products/bpmn-engine}} for further evaluation.
 
@@
 
+In this paper, we presented a system architecture and prototypical implementation for connecting process execution with blockchain technology.
+While keeping the process execution off-chain, we developed an approach of inter-process communication using the Ethereum blockchain as a messaging channel.
+Having a permanent ledger as the underlying data structure storing messages, faults and misunderstandings can be traced back to their origin and responsibilities are disclosed.
+
+Building on the findings of this paper, improvements regarding runtime and execution costs open up a wide area of possible future work on the topic.
+
+Currently, blockchain technology is most widely used to handle monetary transactions.
+Instead of shifting assets between partners, however, we are using the blockchain to shift \textit{responsibilities}.
+Given the similar nature of the two, we speculate that this topic is of future relevance.
 %

### 2018-07-25 paper/paper.tex
Small review changes

@@
 This technology is commonly used to realize virtual currencies, also called cryptocurrencies.
-Ethereum is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
+Ethereum \cite{wood2014ethereum} is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
 Smart contracts are small programs, which are ran by the Blockchain network. They have very limited processing power, but they enable the execution of code which has a commonly known state.
@@
 
-The interaction of the components can be seen in Figure \ref{fig:system_diagram}.
+The structure of components for one organization can be seen in Figure \ref{fig:system_diagram}.
 

### 2018-07-25 paper/paper.tex
write paper structure in introduction

@@
 %What are our results? (briefly)
+
+The rest of this paper is structured as follows: In Section 2 we will discuss concepts and technologies required for our work.
+In Section 3 we will present our use case and our solution concept.
+Section 4 presents our implementation and tools.
+In Section 5 we evaluate our solution.
+Finally, Section 6 will present future work and Section 7 will conclude the paper.
 

### 2018-07-25 paper/paper.tex
rework orchestration and choreography section

@@
 
+% TODO include example here (collab model from weber paper)
 \section{Preliminary}
-In the following section we present concepts and technologies that are related to our concept.
+In the following section we present concepts and technologies that are related to our work.
 
@@
 % TODO improve wording
-When speaking about a Buisiness Process with multiple participants, there are generally two types of perspectives the Process Model can have: Orchestrations and Choreographies.
-Orchestrations view the Process from a central perspective, and contain only one main pool which the process is focused around. 
-They describe the internal process of an organization represented by the pool.
-External communication partners can be included as pools aswell, however their internal processes are not modeled.
-This gives the model a clear state and order in which it has to be executed.
+% TODO reference Weskes book or smth
+Buisiness Processes with multiple participants are modeled using collaboration models, an example can be seen in Figure X. % TODO reference example here
+These collaboration models can be implemented in two variants: As orchestrations, or as choreographies.
+Orchestrations view the Process from a central perspective, most commonly either the central pool which the collaboration focuses on, or the process initiator.
 The main pool inhibits the role of a mediator or manager, dictating and guiding the execution.
+Thus the process has a clear, well-defined order in which tasks have to be executed.
+This also means, that the process always has a clear state of execution.
 
 In a choreography, the participants are much more independent. 
-There is no clear order or state, because the participants are acting and communicating independent of others.
-An orchestration includes all public processes of each pool, as well as the communication between the processes.
+Each participant is its own seperate entity in the implemenation, leading to asynchronous execution and communication.
+Thus, there is also no clear order or state, because the participants are acting and communicating independent of others.
 
-One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the interpretation of orchestration and choreography.
-Weber et al. implement choreographies by means of a central mediator/monitor contract.
-Thus every step in the process is managed by this central contract.
+One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the way we implement collaboration models.
+Weber et al. implement choreographies by means of a central mediator/monitor contract, where every step in the process is managed by this central contract.
 The contract also holds an internal state of the process.
-By our interpretation of the terms, this would not be a choreography but an orchestration.
-Therefore we wanted to implement a solution, which models each pool seperately as their own entity, including having their own contracts.
-Our goal is to decrease the amount of trust needed between the communication partners.
+As explained above, this means they realize the collaboration model with an orchestration.
+Thus, our goal was to implement the collaboration models as choreographies.
+Therefore we developed a solution, which models each pool seperately as their own entity, including having their own contracts.
+This decreases the amount of trust needed between the communication partners.
 By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.

### 2018-07-25 paper/paper.tex
add more explanation to blockchain

@@
 They can receive and send money, store information locally and emit events on the blockchain ledger.
+These events contain pieces of information that are permanently stored publicly on the blockchain.
+External programs can watch, and react to, these events.
 When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
@@
 This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
+Because of the gas limit and high price, the computational power of smart contracts is very limited.
+Smart contracts can also not communicate with anything outside the blockchain.
 %TODO short text on the paper which shows smart contract examples

### 2018-07-25 paper/paper.tex
clarify event throws, correct a phrase

@@
 
+% TODO search for more papers, such as Optimized execution of business processes on blockchain
 \subsection{Prior Work on Business Processes on the Blockchain}
@@
 
-%basic understanding/ intuition
-%-> make orchestration possible
-
-% Decentralized contracts vs. central monitor
-% Engine on chain vs. message channel
-
-%use one contuous example
-
-%visualizations !!
+\section{Requirements}
+% refer to presentation here
+% TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln
 
@@
 We assume that all participating organizations use a process engine to execute their private processes.
-When a throw event is triggered within a process engine, a \emph{throw event function} is called on an instance contract and the corresponding \emph{catch event function} is called on the instance contract of the organization responsible for catching the event.
-Thus, the public processes of all organizations are recorded on the blockchain.
+When a throw event is triggered within a process engine, the process engine calls the \emph{throw event function} on an instance contract and the corresponding \emph{catch event function} is called on the instance contract of the organization responsible for catching the event.
+Thus, all communication between organizations is recorded on the blockchain.
 
@@
 %TODO correctly show that the address is passed instead of using msg.sender
-When a throw event is triggered in the process engine of organization $A$, the corresponding \emph{throw event function} is called on the instance contract of the collaboration partner $B$.
+When a throw event is triggered in the process engine of organization $A$, the process engine of $A$ calls the corresponding \emph{throw event function} on the instance contract of organization $A$.
 In the instance contract of $A$ an authorization is performed by looking up the sender address in the access contract of $A$.

### 2018-07-25 paper/paper.tex
clarify per-company-setup

@@
 An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
-Additionally, the user-to-role and and task-to-role mappings have to be updated, to allow verification of users during the process execution.
+Additionally, the user-to-role and and task-to-role mappings have to be updated (via the \emph{giveRights} and \emph{assignRole} functions), to allow verification of users during the process execution.
 A diagram of this process can be seen in Figure \ref{fig:initialization}.

### 2018-07-25 paper/paper.tex
add todos, correct typo
imporve confidence

@@
 An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.
+% TODO explain how payload could look like
 
@@
 
+% TODO include screenshot
 \subsubsection{Armadillo}
@@
 Internally, calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
-We decide to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
+We decided to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
 The README in our repository describes how to use the application.
@@
 Further research thus could be invested into a more decentralized instantiation, where each participant pays for its own instance contract creation.
-One approach we discussed, but did not have the time to implement, would be to have the intiator emit a specific instance creation event that each other participant would listen to.
+One apporach worth considering is to have the intiator emit a specific instance creation event that each other participant would listen to.
 Then, a trigger could be implemented, that calls the \texttt{createInstance} method as soon as the event is received.

### 2018-07-29 paper/paper.tex
Rework introduction

@@
 	In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
-	We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.
+	We present smart contract system for inter-process communication, as well as a user interface for connecting business processes and smart contracts.
+	While our solution is not production-ready in terms of transaction costs, it describes a basis for untrusted messaging via the blockchain without a central controlling party.
 
@@
 %
-%
-%
-% TODO casing of headlines (capital)
 \section{Introduction}
@@
 
+% BPM
+Business Process Management (BPM) allows organizations to identify, structure and understand the tasks and processes they employ to achieve their business goals.
+%Process Models
+In BPM, Process models are used to document how these goals can be reached, visually describing the participants, activity flow and data objects involved.
+By sharing process models with their employees, organizations can ensure a common understanding of the work that needs to be done.
+
 % What is BPMN?
-The Business Process Model Notation (BPMN) enables detailed documentation of business processes.
-This is used to realize complex inter-business processes which involve vast communication structures.
-One common problem is that within these processes the parties have to trust each other.
+Business Process Model and Notation (BPMN) is a standard notation for process models \cite{omg2014bpmn}.
+It provides building blocks for the modeling of complex intra- and inter-business processes.
+As BPM is not limited internal procedures, but also considers communication with external partners, BPMN can be used to model the message exchange needed for sucessful cooperation.
+
+% Trust
+The basis for inter-process communication is that all involved parties trust each other.
+Companies can enter contracts to safeguard themselves against possibly malicious partners, but it can still lead a lot of overhead to claim their rights in case of a contract infringement.
+Further problems arise when multiple parties are involved in a process:
+The more partners there are, the more difficult it becomes to track faults and misunderstandings in the communication.
+
 % What is Blockchain?
-
-With the increasing spread of Blockchain technology, this problem could be rectified.
-A Blockchain is a decentralized information-storage network.
+With the help of the emerging Blockchain technology, these problems can be resolved.
+A Blockchain is a decentralized information storage network.
 Information is stored in blocks, which are chained together via cryptograhic means.
-This means, that many participants can agree on a common public state of information without trusting each other.
-This technology is commonly used to realize virtual currencies, also called cryptocurrencies.
-Ethereum \cite{wood2014ethereum} is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
-Smart contracts are small programs, which are ran by the Blockchain network. They have very limited processing power, but they enable the execution of code which has a commonly known state.
+In this network, many participants can agree on a public common state of information without trusting each other.
+Blockchain technology is commonly used to realize virtual currencies, also called cryptocurrencies.
+Ethereum \cite{wood2014ethereum} is one implementation of the Blockchain concept which also realizes a feature called smart contracts.
+Smart contracts are small programs that are executed by the nodes in the Blockchain network.
+They have very limited processing power, but they enable the execution of code which has a commonly known state.
 
 %What problems are there with BPMN that can be solved with Blockchain?
-The problem of needing to trust each other when collaborating in a business process can be addressed by applying the benefits of blockchain technology.
-The Blockchain be used in several ways to facilitate trusted communication between untrusted parties.
+Blockchain features can be used to facilitate trusted communication between untrusted parties in Business Process Management.
+% What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
+Existing approaches aim to bring BPM functionality to the Ethereum Blockchain utilizing smart contracts.
+Weber et al. \cite{weber2016untrusted}, e.g., realize process orchestrations on the Blockchain using a smart contract as the mediator for messages and execution state.
+% What is our general Idea?
+We expand on the work of Weber et al. and implement process choreographies, where instead of one central mediator, each party provides their own smart contracts.
+Communication then happens directly between the partner's contracts instead of going through a central instance.
 
-% What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
-Current approaches aim to convert the functionality of traditional BPMN Engines to smart contracts on the Ethereum Blockchain.
+% Structure
+The rest of this paper is structured as follows: In Section \ref{preliminary} we will discuss concepts and technologies required for our work, and introduce our use case.
+In Section \ref{solutionapproach} we will present the solution requirements and concepts.
+Section \ref{implementation} describes our contract and tool implementations.
+In Section \ref{evaluation} we evaluate our solution.
+Finally, Section \ref{futurework} will present future work and Section \ref{conclusion} will conclude the paper.
 
-Caterpillar~\cite{lopez2017caterpillar} features the implementation of most common BPMN elements.
-It enables the transformation of BPMN Models to smart contracts, which can be deployed and executed on the Blockchain.
-
-% TODO write more here
-Weber et al.~\cite{weber2016untrusted} realize Orchestrations on the Blockchain.
-
-%What is our general Idea?
-We want to expand on the work of Weber et al.
-and implement true choreographies.
-In their current approach they are using one central smart contract called a mediator / monitor which manages the Orchestration state.
-We will have a set of smart contracts for every party, which will then communicate with each other to realize the choreography.
-%What are our results? (briefly)
-
-The rest of this paper is structured as follows: In Section 2 we will discuss concepts and technologies required for our work.
-In Section 3 we will present our use case and our solution concept.
-Section 4 presents our implementation and tools.
-In Section 5 we evaluate our solution.
-Finally, Section 6 will present future work and Section 7 will conclude the paper.
-
+\section{Preliminary} \label{preliminary}
 % TODO include example here (collab model from weber paper)
-\section{Preliminary}
 In the following section we present concepts and technologies that are related to our work.
@@
 %display the shortcomings
+
+Caterpillar~\cite{lopez2017caterpillar} is an implementation of a process engine using smart contracts, handling the most common BPMN elements.
+It also allows a translation of BPMN Models to smart contracts, which can be deployed and executed directly on the Ethereum Blockchain.
+
 \cite{lopez2017caterpillar} presents an open-source implementation of an Ethereum-based Business Process Management System.
@@
 
-\section{Solution approach}
+\section{Solution Approach} \label{solutionapproach}
 We propose a system design, that allows choreographies to be executed publicly on the blockchain.
@@
 
-\section{Requirements}
+\subsection{Requirements}
 % refer to presentation here
@@
 
-\subsection{System overview}
+\subsection{System Overview}
 \begin{figure}
@@
 
-\subsection{Per company setup}
+\subsection{Per-Company Setup}
 \begin{figure}
@@
 
-\subsection{Interaction setup}
+\subsection{Interaction Setup}
 \begin{figure}
@@
 
-\subsection{Sending messages}
+\subsection{Sending Messages}
 \begin{figure}
@@
 
-\section{Implementation}
+\section{Implementation} \label{implementation}
 
@@
 
-\section{Evaluation}
+\section{Evaluation} \label{evaluation}
 
@@
 
-\section{Future Work}
+\section{Future Work} \label{futurework}
 
@@
 
-\section{Conclusion}
+\section{Conclusion} \label{conclusion}
 

### 2018-07-29 paper/paper.tex
Work on choreographies and blockchain sections

@@
 \section{Introduction}
-% TODO: rewrite introduction
-
-% Establish common ground with reader Worth readers time? Give some results
-
-% Write it once at the start, then rewrite at the end
-% use it to guide paper
-
-% Important -> this structure will be expected
-
-% Context (Topic / Terminology)
-% Problem & Relevance (Problem - Costs / Current state - Gain)
-% Related Work (Existing solutions / Shortcomings)
-% Goals / Claims (Contribution, Sketch Results)
-% Paper structure (The remainder of this paper is structured as follows ...)
-
 % BPM
@@
 \section{Preliminary} \label{preliminary}
-% TODO include example here (collab model from weber paper)
+
 In the following section we present concepts and technologies that are related to our work.
 
-\subsection{Orchestrations and Choreographies}
+\subsection{Process Interaction}
 
-% TODO improve wording
-% TODO reference Weskes book or smth
-Buisiness Processes with multiple participants are modeled using collaboration models, an example can be seen in Figure X. % TODO reference example here
-These collaboration models can be implemented in two variants: As orchestrations, or as choreographies.
-Orchestrations view the Process from a central perspective, most commonly either the central pool which the collaboration focuses on, or the process initiator.
-The main pool inhibits the role of a mediator or manager, dictating and guiding the execution.
-Thus the process has a clear, well-defined order in which tasks have to be executed.
-This also means, that the process always has a clear state of execution.
+Managing interactions between process participants is a core feature of BPM
+\cite{Weske2012}. % TODO improve with book
+Business processes with multiple participants can be modeled in BPMN using collaboration models.
+Such models include the businesses' \emph{public processes}, i.e., the BPMN tasks and events describing the sending and receiving of messages, as well as the message flow between the participants.
+While not directly part of the interaction, they can also depict \emph{private processes}, i.e., tasks and control flows that are internally executed before or after sending or receiving a message.
+An example can be seen in Figure \ref{collaborationexample}. % TODO reference example here
 
-In a choreography, the participants are much more independent.
-Each participant is its own seperate entity in the implemenation, leading to asynchronous execution and communication.
-Thus, there is also no clear order or state, because the participants are acting and communicating independent of others.
+The execution of a collaboration model can be implemented either as an \emph{orchestration}, or as a \emph{choreography}.
+In a process orchestration, the execution is controlled by a central instance.
+Adopting the role of a mediator or manager, this central instance dictates and guides the execution.
+Thus, the execution has a well-defined order of tasks and a clear execution state.
+In a choreography, on the other hand, the participants are acting more independently.
+Communication and execution is not handled by a central instance, but rather by each participant on their own.
+Messages are passed asynchronously without a controlling channel.
+As a result, there is no clear execution state, because each participant drives their own execution.
 
-One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the way we implement collaboration models.
+\subsection{Blockchain}
+
+A blockchain is a distributed ledger that allows users to find a consensus in decentralized applications.
+Information is stored in a linked list of blocks and shared between all participants, i.e., all nodes in a decentralized computer network.
+By only allowing new blocks to be appended to the list, a non-rewritable history is created, that at the same time represents the "truth", the common state all nodes in the network agree on.
+There are multiple approaches of determining who is allowed to append a new block, altering the state.
+The most common one, currently employed for example by Bitcoin \cite{nakamoto2008bitcoin} and Ethereum \cite{wood2014ethereum}, is called \emph{proof of work}:
+Each new block has to contain a signature that verifies the block order.
+The signature is created using data from the preceding block and is by design mathematically hard to calculate, but easy to verify.
+On the one hand, this results in a race between so called \emph{mining} nodes who try and calculate such a signature, as the first valid signature verifies the new block's position and stores it's data on the ledger.
+Mining nodes get rewarded for finding such signatures, creating an incentive for continuous appending of new blocks and keeping the blockchain alive.
+On the other hand, other nodes can easily verify the signature and come to a consensus regarding the latest state.
+If the same block is signed at the same time, a fork of the blockchain is created, where two versions of the blockchain exist at the same time.
+Consensus is then reached when new blocks are appended, propagating the longest blockchain within the network until it is accepted by all parties.
+
+Blockchain technology is mainly used for cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
+In more recent developments however, they are used as a foundation for a number of other decentralized applications.
+Ethereum \cite{wood2014ethereum} is a platform that uses a blockchain as the underlying system, but further allows users write and execute code in the form of \emph{smart contracts}.
+Smart contracts are Turing complete code artifacts that can be deployed on the blockchain and are accessible by accounts in the Ethereum platform.
+When called by a user account or another contract, they can perform calculations, send or receive money, or store information on the blockchain ledger either directly or in the form of \emph{events}.
+Events are publicly visible and can be watched by off-chain applications, allowing external programs to react to blockchain state changes.
+This would otherwise not be possible, ss smart contracts can not communicate with anything outside the blockchain.
+
+When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
+Contracts deplete gas for each operation and return excess gas back to the user.
+This ensures that contracts are not running for an unlimited amount of time, avoiding a dead lock of the platform.
+Computations on the blockchain are expensive in order to avoid unnecessary operations, as all operations have to be performed by each node in the network.
+Because of the gas limit and high execution cost, the computational power of smart contracts is limited.
+
+Smart contracts are executed in the \emph{Ethereum virtual machine (EVM)}.
+As such, they contain byte code that is interpreted by the VM.
+When developing smart contracts, there are multiple languages that compile to EVM bytecode, the most prominent one currently being \emph{Solidity}\footnote{\url{https://github.com/ethereum/solidity}}, which we also chose to implement our protoype.
+Xu et al. present patterns and examples for Solidity programming in \cite{xu2018pattern}, which we used as orientation during development.
+
+% TODO search for more papers, such as Optimized execution of business processes on blockchain
+\subsection{Prior Work on Business Processes on the Blockchain}
+In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
+Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
+They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
+They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
+In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
+
+One of the main ways our solution differs from the solution of Weber et al. \cite{weber2016untrusted} is in the way we implement collaboration models.
 Weber et al. implement choreographies by means of a central mediator/monitor contract, where every step in the process is managed by this central contract.
@@
 
-% TODO write about public and private processes
-
-\subsection{Blockchain}
-A blockchain is a distributed ledger that allows users to find a concensus in decentralized applications.
-It works by splitting information into blocks that are connected as a linked list.
-%TODO proof of work is only one possibility
-%TODO explain more in depth?
-Each block has to be signed in a way that is mathematically hard to calculate, but easy to verify.
-Therefore users can verify if their local blockchain is valid.
-If the same block is signed at the same time, a fork of the blockchain can happen, i.e. two versions of the same blockchain exist at the same time.
-A concensus is reached by propagating the longest blockchain within the network until it is accepted by all parties of the network.
-
-%TODO reference original blockchain paper
-Blockchain technology is used in cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
-The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
-Ethereum \cite{wood2014ethereum} is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
-Smart contracts are Turing complete code artifacts, that can be deployed on the blockchain and have an interface that is callable by users.
-They can receive and send money, store information locally and emit events on the blockchain ledger.
-These events contain pieces of information that are permanently stored publicly on the blockchain.
-External programs can watch, and react to, these events.
-When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
-Contracts deplete gas for each operation and return excess gas back to the user.
-This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
-Because of the gas limit and high price, the computational power of smart contracts is very limited.
-Smart contracts can also not communicate with anything outside the blockchain.
-%TODO short text on the paper which shows smart contract examples
-%TODO short text on solidity
-
-% TODO search for more papers, such as Optimized execution of business processes on blockchain
-\subsection{Prior Work on Business Processes on the Blockchain}
-In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
-Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
-They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
-They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
-In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
 %TODO highlight lack of access right explanation and problem of central contract?
@@
 %no choreographies / lanes supported, all tasks / transitions are managed on-chain through process %contract
+
+\subsection{Use Case}
+
+% TODO include example here (collab model from weber paper)
+\begin{figure}
+	\label{collaborationexample}
+\end{figure}
 
@@
 In our implementation, a company's factory contract also knows the address of the company's access contract for convenience.
-Additionally, it stores the addresses of created instances, mapped by a \textit{choreography instance ID}, i.e., an ID that is shared between all choreography participants for each instance of the shared choreography.
+Additionally, it stores the addresses of created instances, mapped by a \emph{choreography instance ID}, i.e., an ID that is shared between all choreography participants for each instance of the shared choreography.
 
@@
 To avoid communication errors at runtime, it should not be possible to call \texttt{createInstance} before all required factory addresses are set.
-Finally, there is one minor implementation difference depending on whether a participant is the \textit{choreography initiator} -- the participant to manually start the choreography instance by sending a request -- or instead is starting its instance as a response to another participant's request: % TODO arrgh bessere formulierung
+Finally, there is one minor implementation difference depending on whether a participant is the \emph{choreography initiator} -- the participant to manually start the choreography instance by sending a request -- or instead is starting its instance as a response to another participant's request: % TODO arrgh bessere formulierung
 The initiator needs to generate the choreography instance ID inside of its \texttt{createInstance} function, and pass it to all its interaction partners.
@@
 Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
-Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \textit{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
+Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
 A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/blob/master/presentation/armadillo-screencast.mp4}.
@@
 When evaluating blockchain implementations, the underlying system comes with new aspects that need to be considered.
-First, computation and data storage on the blockchain needs to be paid for in \textit{transaction fees}.
-In Ethereum, the unit \textit{gas} was introduced as a way of having consistent fee pricing in spite of fluctuating Ether prices.
+First, computation and data storage on the blockchain needs to be paid for in \emph{transaction fees}.
+In Ethereum, the unit \emph{gas} was introduced as a way of having consistent fee pricing in spite of fluctuating Ether prices.
 
@@
 However, the instantiation cost that is currently paid by the initiator appears to be problematic.
-As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \textit{gas limit}, the maximum amount of gas that can be spent per transaction.
+As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{gas limit}, the maximum amount of gas that can be spent per transaction.
 Even if that is not the case, a high gas cost is still a problem, since transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times.
@@
 In our case, we put effort into making the message exchange secure by adding multiple steps of access verification using the access contracts.
-Access contracts themselves, however, only implement access verification by comparing the sender address with the address the contract was deployed with (the \textit{owner} address).
+Access contracts themselves, however, only implement access verification by comparing the sender address with the address the contract was deployed with (the \emph{owner} address).
 As the owner can give and remove access rights freely, another layer of off-chain security might make sense here to restrict the owner account from unwanted access.
@@
 Currently, blockchain technology is most widely used to handle monetary transactions.
-Instead of shifting assets between partners, however, we are using the blockchain to shift \textit{responsibilities}.
+Instead of shifting assets between partners, however, we are using the blockchain to shift \emph{responsibilities}.
 Given the similar nature of the two, we speculate that this topic is of future relevance.

### 2018-07-29 paper/paper.tex
Add use case

@@
 % What is BPMN?
-Business Process Model and Notation (BPMN) is a standard notation for process models \cite{omg2014bpmn}.
+Business Process Model and Notation (BPMN) is a standard notation for process models~\cite{omg2014bpmn}.
 It provides building blocks for the modeling of complex intra- and inter-business processes.
@@
 Blockchain technology is commonly used to realize virtual currencies, also called cryptocurrencies.
-Ethereum \cite{wood2014ethereum} is one implementation of the Blockchain concept which also realizes a feature called smart contracts.
+Ethereum~\cite{wood2014ethereum} is one implementation of the Blockchain concept which also realizes a feature called smart contracts.
 Smart contracts are small programs that are executed by the nodes in the Blockchain network.
@@
 Blockchain features can be used to facilitate trusted communication between untrusted parties in Business Process Management.
-% What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
+% What approaches exist currently (Caterpillar~\cite{lopez2017caterpillar}, Untrusted paper~\cite{weber2016untrusted})
 Existing approaches aim to bring BPM functionality to the Ethereum Blockchain utilizing smart contracts.
-Weber et al. \cite{weber2016untrusted}, e.g., realize process orchestrations on the Blockchain using a smart contract as the mediator for messages and execution state.
+Weber et al.~\cite{weber2016untrusted}, e.g., realize process orchestrations on the Blockchain using a smart contract as the mediator for messages and execution state.
 % What is our general Idea?
@@
 While not directly part of the interaction, they can also depict \emph{private processes}, i.e., tasks and control flows that are internally executed before or after sending or receiving a message.
-An example can be seen in Figure \ref{collaborationexample}. % TODO reference example here
+An example can be seen in Figure \ref{fig:collaboration}.
 
@@
 There are multiple approaches of determining who is allowed to append a new block, altering the state.
-The most common one, currently employed for example by Bitcoin \cite{nakamoto2008bitcoin} and Ethereum \cite{wood2014ethereum}, is called \emph{proof of work}:
+The most common one, currently employed for example by Bitcoin~\cite{nakamoto2008bitcoin} and Ethereum~\cite{wood2014ethereum}, is called \emph{proof of work}:
 Each new block has to contain a signature that verifies the block order.
@@
 
-Blockchain technology is mainly used for cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
+Blockchain technology is mainly used for cryptocurrencies, most notably Bitcoin~\cite{nakamoto2008bitcoin}.
 In more recent developments however, they are used as a foundation for a number of other decentralized applications.
-Ethereum \cite{wood2014ethereum} is a platform that uses a blockchain as the underlying system, but further allows users write and execute code in the form of \emph{smart contracts}.
+Ethereum~\cite{wood2014ethereum} is a platform that uses a blockchain as the underlying system, but further allows users write and execute code in the form of \emph{smart contracts}.
 Smart contracts are Turing complete code artifacts that can be deployed on the blockchain and are accessible by accounts in the Ethereum platform.
@@
 When developing smart contracts, there are multiple languages that compile to EVM bytecode, the most prominent one currently being \emph{Solidity}\footnote{\url{https://github.com/ethereum/solidity}}, which we also chose to implement our protoype.
-Xu et al. present patterns and examples for Solidity programming in \cite{xu2018pattern}, which we used as orientation during development.
+Xu et al. present patterns and examples for Solidity programming in~\cite{xu2018pattern}, which we used as orientation during development.
 
-% TODO search for more papers, such as Optimized execution of business processes on blockchain
 \subsection{Prior Work on Business Processes on the Blockchain}
-In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
+In~\cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
 Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
-They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
-They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
-In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
+The mediator is also responsible for role management, i.e., participants can register users to certain roles with the mediator, who verifies these roles at runtime.
+The architecture features factory contracts, which are responsible for deploying instance contracts for each process instance.
+For integrating blockchain and BPM applications, the concept of \emph{triggers} is introduced: Applications that watch events on the blockchain and trigger external API calls.
 
-One of the main ways our solution differs from the solution of Weber et al. \cite{weber2016untrusted} is in the way we implement collaboration models.
-Weber et al. implement choreographies by means of a central mediator/monitor contract, where every step in the process is managed by this central contract.
-The contract also holds an internal state of the process.
-As explained above, this means they realize the collaboration model with an orchestration.
-Thus, our goal was to implement the collaboration models as choreographies.
-Therefore we developed a solution, which models each pool seperately as their own entity, including having their own contracts.
-This decreases the amount of trust needed between the communication partners.
-By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.
+We built our implementation based on these concepts.
+However, our solution differs from the solution in~\cite{weber2016untrusted} in the way we realize the execution of collaboration models.
+As stated before, Weber et al. employ the central mediator contract, managing execution steps and internal state of the collaboration, achieving the orchestration of a business process collaboration.
+Our goal on the other hand was to implement the collaboration as a choreography, where each participant is represented by their own contracts, and is able to verify the integrity of their interaction partners.
+Thus, a central mediator is no longer needed, also resolving the question of who is responsible for the development, deployment and maintenance of the mediator contract.
 
-%TODO highlight lack of access right explanation and problem of central contract?
+In order to achieve BPMN-to-Solidity compilation,~\cite{weber2016untrusted} also describes translation rules to transform BPMN elements to Solidity code.
+In~\cite{banuelos2017optimized}, these translation rules are further optimized to reduce Ethereum transaction costs and runtime. %TODO is this correct?
 
-%we build on:
-%factories \& instances
-%registering users to roles
-%triggers
-%the model they used (originally from Fdhila et al)
+We have not made an automated translation our primary goal.
+Instead, we focussed on designing an architecture that allows for the above mentioned choreography implementation.
+However, we believe that an at least semi-automatic translation process can be derived from our results.
 
-%we don\'t:
-%do bpmn solidity translation
-%use one central contract instance
+Caterpillar~\cite{lopez2017caterpillar} is an open source implementation of a process engine using smart contracts, handling the most common BPMN elements.
+Building on the BPMN-to-Solidity compilation from~\cite{weber2016untrusted}, it integrates translation, deployment and execution of BPMN models in the form of smart contracts directly on the Ethereum Blockchain.
+It also allows a translation of BPMN Models to smart contracts, which can be deployed and executed directly on the Ethereum Blockchain.
+Processes can be started and executed via a user interface, which encapsulates the calls the generated Solidity code in the background.
 
-%summarize Caterpillar
-%acknowledge their Work
-%display the shortcomings
-
-Caterpillar~\cite{lopez2017caterpillar} is an implementation of a process engine using smart contracts, handling the most common BPMN elements.
-It also allows a translation of BPMN Models to smart contracts, which can be deployed and executed directly on the Ethereum Blockchain.
-
-\cite{lopez2017caterpillar} presents an open-source implementation of an Ethereum-based Business Process Management System.
-It implements BPMN-to-Solidity compilation and thereby tracks the state of process executions on the blockchain.
-Processes can be started and executed via a user interface, which calls the generated Solidity code in the background.
-
-%describes components and architecture of engine
-%automatic bpmn solidity translation
-%no choreographies / lanes supported, all tasks / transitions are managed on-chain through process %contract
+Our approach is different in that we do not try to use the Ethereum platform as a process engine, but rather use it only for message passing, and integrate it with an off-chain process engine.
+Caterpillar also currently does not support the execution of process interactions.
 
@@
 
-% TODO include example here (collab model from weber paper)
+Since we build on a lot of the work in~\cite{weber2016untrusted}, we decided to also continue with the example collaboration\footnote{A supply chain scenario reported originally in~\cite{fdhila2015collaborative}, which was simplified in~\cite{weber2016untrusted}.} used there.
+Because we implemented contracts for each participant, we needed to expand the collapsed pool for the \emph{Bulk Buyer}, and add tasks and events for the corresponding public process.
+We added a new lane to the \emph{Manufacturer's} process for demonstration of the role management we implemented.
+The result is depicted in Figure \ref{fig:collaboration}.
+
+When we present the implementation, the tasks that are modeled as BPMN message sends in the collaboration model will instead be modeled as \emph{BPMN service tasks} in the separate processes.
+This decision is based on the notion that in our implementation, all sends are a call to the Ethereum platform, which acts as the external service and takes over the actual messaging.
+This implementation detail is not relevant in the collaboration view, though, where we are concerned with the interactions.
+
 \begin{figure}
-	\label{collaborationexample}
+	\centering
+	\includegraphics[width=\textwidth]{fig/collaboration.eps}
+	\caption{Supply chain scenario from~\cite{weber2016untrusted} (modified).}
+	\label{fig:collaboration}
 \end{figure}
@@
 
-%TODO reference "trigger" from Untrusted paper
-Each organization uses a \emph{trigger} that continuously listens to catch events.
+Each organization deploys a \emph{trigger} application that continuously listens to catch events (as described in \cite{weber2016untrusted}).
 If a catch event is observed, this information is relayed to the process engine to handle the event.
@@
 To this end, the factory contract source code needs to contain the definition of the company's instance contract.
-This closely follows the factory contract pattern used in \cite{weber2016untrusted}, and described as Pattern 14 in \cite{xu2018pattern}.
+This closely follows the factory contract pattern used in~\cite{weber2016untrusted}, and described as Pattern 14 in~\cite{xu2018pattern}.
 
@@
 Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partner's access contract.
-Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in \cite{xu2018pattern}.
+Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in~\cite{xu2018pattern}.
 
@@
 Each company deploys an access contract that holds information about the roles and permissions of the company's employees.
-Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from \cite{xu2018pattern}.
+Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from~\cite{xu2018pattern}.
 It allows decoupling the roles and permissions from the actual contract instances, allowing for a simple modification at runtime.
@@
 Finding optimized, less costly (both in computation cost and storage cost) approaches is part of future work.
-One other approach we thought of is based on Pattern 5 of \cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify one's role.
+One other approach we thought of is based on Pattern 5 of~\cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify one's role.
 
@@
 We decided to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
-The README in our repository describes how to use the application.
+The \texttt{README} in our repository describes how to use the application.
 
@@
 \section{Future Work} \label{futurework}
+% TODO merge duplicated content
 
@@
 Since the contracts all share the same patterns,  this is a prime candidate for automation.
-A possible implementation could use a rule-based approach for translating the choreography model, similar to \cite{lopez2017caterpillar}.
+A possible implementation could use a rule-based approach for translating the choreography model, similar to~\cite{lopez2017caterpillar}.
 This would then automatically generate Solidity code for the access and factory contracts.
@@
 
-In related work \cite{lopez2017caterpillar}, process logic was executed on the blockchain.
+In related work~\cite{lopez2017caterpillar}, process logic was executed on the blockchain.
 As we decided for a hybrid approach, using a process engine for execution and the Ethereum blockchain for traceable message passing, we implemented a mock process engine in our application.

### 2018-07-30 paper/paper.tex
Merge duplicated further work parts

@@
 \section{Future Work} \label{futurework}
-% TODO merge duplicated content
 
@@
 
-In the evaluation, we realized that the instantiation cost currently is too high for our system to be used in a productive environment.
+During evaluation, we saw that the instantiation costs are very high, have a potential to hit the gas limit in larger choreographies and also have to be paid by the initiator.
+These problems need to be addressed before our solution is feasible for production use.
 Further research thus could be invested into a more decentralized instantiation, where each participant pays for its own instance contract creation.
 One apporach worth considering is to have the intiator emit a specific instance creation event that each other participant would listen to.
-Then, a trigger could be implemented, that calls the \texttt{createInstance} method as soon as the event is received.
-
-During evaluation, we saw that the instantiation costs are very high, have a potential to hit the gas limit in larger choreographies and also have to be paid by the initiator.
-These problems need to be addressed before our solution is viable for production use.
-One possbile way to distribute the costs among the participants makes use of triggers on the factory contracts.
-Instead of creating all instance contracts transitively, the factory contract would have a method for accepting requests for instantiation.
-The process engine could then react to such a call via a trigger, and call the instantiation method.
+The process engine could then react to such an event with the help of a trigger, and call the \texttt{createInstance} method.
 Then the other factory would have to be notified that the instantiation was successful.
@@
 
-As stated earlier, there possibly are better ways of implementing a role-based access control inside a smart contract.
-We decided for a simple mapping-based approach, which requires a relatively large amount of memory.
+As stated earlier, there probably are better ways of implementing role-based access control in a smart contract.
+We decided for a simple mapping-based approach, which requires large amounts of memory.
 Finding approaches that are more suited for blockchain architectures is one direction in which further research could go.
@@
 Our contract implementations are the result of manual, iterative development.
-Having reached the final iteration, we realized that most of the implementation could probably be generated, i.e., from a choreography diagram (or at least from the participant's public processes).
+Having reached the final iteration, we realized that the contracts share common patterns.
+Most of the implementation could probably be generated, i.e., from a choreography diagram (or at least from the participant's public processes).
 The next step would be to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments, e.g., depending on whether the participant is the initiator or not.
 Given such a template, one could work on a contract generation tool that takes a diagram as input and produces factory contract code.
-
-Currently all contracts are written manually.
-Since the contracts all share the same patterns,  this is a prime candidate for automation.
 A possible implementation could use a rule-based approach for translating the choreography model, similar to~\cite{lopez2017caterpillar}.
-This would then automatically generate Solidity code for the access and factory contracts.
 

### 2018-07-30 paper/paper.tex
Add gas table

@@
 \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+% tablespacing
+\renewcommand{\arraystretch}{1.5}
+\setlength\tabcolsep{0.2cm}
 
@@
 
-\section{Evaluation} \label{evaluation}
+\section{Discussion} \label{evaluation}
 
@@
 
-We measured the gas used for each transaction that is executed by the Armadillo tool, and we summed up the gas usage for the different kinds of contracts in the companies in the following table:
+We measured the gas used for each transaction that is executed by the Armadillo tool, and we summed up the gas usage for the different kinds of contracts in the companies in Table \ref{gasusage}:
 
-\begin{tabular}{l|l|l|l}
-	% TODO
-	a & b & c & d
+\begin{table}
+	\centering
+	\caption{Gas used by contracts in the example choreography.} \label{gasusage}
+	\begin{tabular}{|l | c | c | c|}
+		\hline                          & \textbf{Factory} & \textbf{Instance} & \textbf{Sum}       \\
+		\hline \textbf{Bulk Buyer}      & 4,590,569        & 59,396            & 4,649,965          \\
+		\hline \textbf{Manufacturer}    & 129,588          & 124,316           & 253,904            \\
+		\hline \textbf{Middleman}       & 129,586          & 111,189           & 240,775            \\
+		\hline \textbf{Supplier}        & 86,398           & 61,745            & 148,143            \\
+		\hline \textbf{Special Carrier} & 86,376           & 81,945            & 168,321            \\
+		\hline \textbf{Sum}             & 5,022,517        & 438,591           & \textbf{5,461,108} \\ \hline
 	\end{tabular}
+\end{table}
 
@@
 However, the instantiation cost that is currently paid by the initiator appears to be problematic.
-As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{gas limit}, the maximum amount of gas that can be spent per transaction.
-Even if that is not the case, a high gas cost is still a problem, since transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times.
-% TODO explain?
+As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block.
+%Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times.
+% TODO why again?
 
@@
 As the owner can give and remove access rights freely, another layer of off-chain security might make sense here to restrict the owner account from unwanted access.
-
-%Time for one instance
-%Setup difficulty
 

### 2018-07-30 paper/paper.tex
Add armadillo screenshot

@@
 
-% TODO include screenshot
 \subsubsection{Armadillo}
 
-As a way of joining process execution with our blockchain architecture, we developed a single page web application in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
+\begin{figure}
+	\centering
+\includegraphics[width=0.9\textwidth]{fig/Armadillo.png}
+\caption{Screenshot of the Armadillo web application.}
+\label{fig:armadillo}
+\end{figure}
+
+As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
 With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
@@
 \end{table}
-
+% TODO add exchange rates and $ price? or propmt users to look it up themselves because of changing gas price?
 Most of the transactions have proven to come with reasonable gas costs.

### 2018-07-30 paper/paper.tex
Fix weske citation

@@
 
-\subsection{Process Interaction}
+\subsection{Business Process Collaboration}
 
-Managing interactions between process participants is a core feature of BPM
-\cite{Weske2012}. % TODO improve with book
-Business processes with multiple participants can be modeled in BPMN using collaboration models.
-Such models include the businesses' \emph{public processes}, i.e., the BPMN tasks and events describing the sending and receiving of messages, as well as the message flow between the participants.
+When businesses work together to reach a common goal, their processes also need to comply with each other.
+Such business-to-business collaborations can also be modeled in BPMN.
+Collaboration models include the businesses' \emph{public processes} (or \emph{behavioral interfaces}~\cite{Weske2012}), i.e., the BPMN tasks and events describing the sending and receiving of messages, as well as the message flow between the participants.
 While not directly part of the interaction, they can also depict \emph{private processes}, i.e., tasks and control flows that are internally executed before or after sending or receiving a message.
@@
 
-The execution of a collaboration model can be implemented either as an \emph{orchestration}, or as a \emph{choreography}.
+Process interoperability needs to be ensured when it comes to executing a collaboration model.
+To this end, there are two different implementation approaches:
+One option is to treat the collaboration like a local, internal process, employing a \emph{process orchestration}.
 In a process orchestration, the execution is controlled by a central instance.
@@
 Thus, the execution has a well-defined order of tasks and a clear execution state.
-In a choreography, on the other hand, the participants are acting more independently.
+
+Another option is to have the participants act more independently.
+In \cite{Weske2012}, Weske describes \emph{process choreographies}, which define and ensure a set of collaboration rules to ensure interoperabiltiy.
+A choreography clarifies the dependencies between the participant's processes and the messages they need to exchange for a successful collaboration.
 Communication and execution is not handled by a central instance, but rather by each participant on their own.
@@
 
-Each organization deploys a \emph{trigger} application that continuously listens to catch events (as described in \cite{weber2016untrusted}).
+Each organization deploys a \emph{trigger} application that continuously listens to catch events (as described in~\cite{weber2016untrusted}).
 If a catch event is observed, this information is relayed to the process engine to handle the event.

### 2018-07-30 paper/paper.tex
Fix minor rephrasing todos

@@
 	\item A \texttt{getAccessAddress} function
-	\item A \texttt{isInstance} function, checking if a given address belongs to an instance created by this factory, for a given choreography instance ID % TODO rephrase?
+	\item A \texttt{isInstance} function used to verify whether an address points to an instance contract created by this factory (for a given choreography ID)
 \end{itemize}
@@
 To avoid communication errors at runtime, it should not be possible to call \texttt{createInstance} before all required factory addresses are set.
-Finally, there is one minor implementation difference depending on whether a participant is the \emph{choreography initiator} -- the participant to manually start the choreography instance by sending a request -- or instead is starting its instance as a response to another participant's request: % TODO arrgh bessere formulierung
+Finally, there is one minor implementation difference depending on whether a participant is the \emph{choreography initiator} (the participant to manually start the choreography instance by sending a request):
 The initiator needs to generate the choreography instance ID inside of its \texttt{createInstance} function, and pass it to all its interaction partners.

### 2018-07-30 paper/paper.tex
Resolve minor annotations from stephan

@@
 We assume that all participating organizations use a process engine to execute their private processes.
-When a throw event is triggered within a process engine, the process engine calls the \emph{throw event function} on an instance contract and the corresponding \emph{catch event function} is called on the instance contract of the organization responsible for catching the event.
+When a throw event is triggered within a process engine, the process engine calls the \emph{throw event function} on an instance contract, which in turn automatically calls the corresponding \emph{catch event function} on the instance contract of the organization responsible for catching the event.
 Thus, all communication between organizations is recorded on the blockchain.
@@
 An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
-Additionally, the user-to-role and and task-to-role mappings have to be updated (via the \emph{giveRights} and \emph{assignRole} functions), to allow verification of users during the process execution.
+Additionally, the user-to-role and and task-to-role mappings have to be updated (via the \emph{giveRights} and \emph{assignRole} functions, respectively), to allow verification of users during the process execution.
 A diagram of this process can be seen in Figure \ref{fig:initialization}.
@@
 To this end, the factory contract source code needs to contain the definition of the company's instance contract.
-This closely follows the factory contract pattern used in~\cite{weber2016untrusted}, and described as Pattern 14 in~\cite{xu2018pattern}.
+This closely follows the factory contract pattern used in~\cite{weber2016untrusted}, and described as pattern 14 in~\cite{xu2018pattern}.
 
@@
 Finding optimized, less costly (both in computation cost and storage cost) approaches is part of future work.
-One other approach we thought of is based on Pattern 5 of~\cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify one's role.
+One other approach we thought of is based on pattern 5 of~\cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify one's role.
 
@@
 However, the instantiation cost that is currently paid by the initiator appears to be problematic.
-As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block.
+As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block, depending on the number of participants involved.
 %Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times.

### 2018-07-30 paper/paper.tex
add requirements

@@
 \subsection{Requirements}
-% refer to presentation here
+
+First, we want to give an overview of the functional and non-functional requirements, that the system has to fulfill.
+
+The systems purpose is to facilitate trusted communication and collaboration between untrusting partners.
+For this, it has to be possible to send messages between partners.
+To ensure security and trust in the system, both partners need a way to verify the authenticity of a message.
+This means that the system has to keep track of users and permissions.
+To keep this maintainable, we will need a user-to-role and role-to-permission mapping.
+This mapping should be flexible, i.e. creatable and modifyable at runtime.
+Of course it also has to be queryable, so that the communicating partners can use it to check the authenticity of messages.
+
+In order to make this system feasible in a production environment, we also require it to be reusable, measurable and cheap.
+This implies keeping the amount of contracts, memory consumption and message calls low.
+Measurability is required for evaluation and monitoring.
+Because all computation done by smart contracts requires a certain amount of gas (and thus money), we want to keep the cost of our implementation as low as possible.
+
 % TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln

### 2018-07-30 paper/paper.tex
Rephrasing

--- 2018-07-30 paper/paper.tex
@@
 In order to achieve BPMN-to-Solidity compilation,~\cite{weber2016untrusted} also describes translation rules to transform BPMN elements to Solidity code.
-In~\cite{banuelos2017optimized}, these translation rules are further optimized to reduce Ethereum transaction costs and runtime. %TODO is this correct?
+Further work~\cite{banuelos2017optimized} tries to optimize the translation process, in turn reducing Ethereum execution costs by reducing required space and operations.
 
@@
 \subsection{Requirements}
-% refer to presentation here
-% TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln
+
+Before presenting the system, want to give an overview of the functional and non-functional requirements it has to fulfill.
+
+The system's purpose is to facilitate trusted communication and collaboration between untrusting partners.
+Therefore, it must be possible to send messages between partners.
+To ensure security and trust in the system, both partners need a way to verify the authenticity of a message.
+Verification is only possible if the system keeps track of users and permissions, i.e., implements a form of role-based access control with a user-to-role and role-to-permission mapping.
+User and permission data has to be accessible at runtime, so that the communicating partners can use it to check the authenticity of messages.
+It should also be possible to modify this data at runtime, to accomodate for changes in the company structure.
+
+In order to make this system feasible in a production environment, we also require it to be reusable, measurable and cheap.
+This implies keeping the implementation small and modular, and keeping it general enough to be used with the processes of different participants.
+Measurability is required for evaluation and monitoring.
+Since all computation done by smart contracts comes with gas costs, we want to keep the cost of our implementation as low as possible.
 

### 2018-07-30 paper/paper.tex
Shorten intro

@@
 	In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
-	We present smart contract system for inter-process communication, as well as a user interface for connecting business processes and smart contracts.
+	We present a smart contract system for inter-process communication, as well as a user interface for connecting business processes and smart contracts.
 	While our solution is not production-ready in terms of transaction costs, it describes a basis for untrusted messaging via the blockchain without a central controlling party.
@@
 %Process Models
-In BPM, Process models are used to document how these goals can be reached, visually describing the participants, activity flow and data objects involved.
-By sharing process models with their employees, organizations can ensure a common understanding of the work that needs to be done.
+In BPM, process models are used to document how these goals can be reached, visually describing the participants, activity flow and data objects involved.
 
 % What is BPMN?
-Business Process Model and Notation (BPMN) is a standard notation for process models~\cite{omg2014bpmn}.
-It provides building blocks for the modeling of complex intra- and inter-business processes.
-As BPM is not limited internal procedures, but also considers communication with external partners, BPMN can be used to model the message exchange needed for sucessful cooperation.
+Business Process Model and Notation (BPMN) is a notation standard for such process models~\cite{omg2014bpmn}.
+It provides building blocks for the modeling of not only internal procedures, but also the message exchange needed for successful communication with external partners.
 
@@
 The basis for inter-process communication is that all involved parties trust each other.
-Companies can enter contracts to safeguard themselves against possibly malicious partners, but it can still lead a lot of overhead to claim their rights in case of a contract infringement.
-Further problems arise when multiple parties are involved in a process:
-The more partners there are, the more difficult it becomes to track faults and misunderstandings in the communication.
+Agreements and contracts can help clarifying the requirements and expectations between partners.
+As soon as multiple parties are involved in the handling of a process, though, it becomes difficult to track faults and misunderstandings in the communication.
 
@@
 With the help of the emerging Blockchain technology, these problems can be resolved.
-A Blockchain is a decentralized information storage network.
-Information is stored in blocks, which are chained together via cryptograhic means.
-In this network, many participants can agree on a public common state of information without trusting each other.
+A Blockchain network is a network of computation nodes sharing a decentralized information storage structure, a \emph{ledger}.
+Inside this ledger, information is stored in blocks, which are chained together via cryptograhic means.
+Nodes in the network can agree on a public common state of information without trusting each other.
 Blockchain technology is commonly used to realize virtual currencies, also called cryptocurrencies.
 Ethereum~\cite{wood2014ethereum} is one implementation of the Blockchain concept which also realizes a feature called smart contracts.
-Smart contracts are small programs that are executed by the nodes in the Blockchain network.
-They have very limited processing power, but they enable the execution of code which has a commonly known state.
+Smart contracts are small programs with limited processing power that are executed by the nodes in the Blockchain network.
 
@@
 % What approaches exist currently (Caterpillar~\cite{lopez2017caterpillar}, Untrusted paper~\cite{weber2016untrusted})
-Existing approaches aim to bring BPM functionality to the Ethereum Blockchain utilizing smart contracts.
-Weber et al.~\cite{weber2016untrusted}, e.g., realize process orchestrations on the Blockchain using a smart contract as the mediator for messages and execution state.
+Approaches exist that aim to bring BPM functionality to the Ethereum Blockchain utilizing smart contracts.
+Weber et al.~\cite{weber2016untrusted} realize process orchestrations on the Blockchain using a smart contract as the mediator for messages and execution state.
 % What is our general Idea?
 We expand on the work of Weber et al. and implement process choreographies, where instead of one central mediator, each party provides their own smart contracts.
-Communication then happens directly between the partner's contracts instead of going through a central instance.
+Communication then happens directly between the partner's contracts instead of passing through a central instance.
 
@@
 Section \ref{implementation} describes our contract and tool implementations.
-In Section \ref{evaluation} we evaluate our solution.
+In Section \ref{evaluation} we discuss our solution.
 Finally, Section \ref{futurework} will present future work and Section \ref{conclusion} will conclude the paper.
@@
 %TODO add emit event in the diagram
-%TODO better formulation
+%TODO rephrasing
 The organizations that did not start the instance creation can detect the new process instance by using their trigger to watch the factory contract.
@@
 The implemented contracts can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/tree/master/armadillo/resources}.
-% TODO repo ist noch private
-% TODO update if repository changes
+% TODO repo & hbox
 
@@
 The implementations can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
-% TODO repo ist noch private
-% TODO update if repository changes
-% TODO overfull hbox
+% TODO repo & hbox
 

### 2018-07-30 paper/paper.tex
Shorten blockchain preliminary

@@
 
-In the following section we present concepts and technologies that are related to our work.
-
 \subsection{Business Process Collaboration}
@@
 Such business-to-business collaborations can also be modeled in BPMN.
-Collaboration models include the businesses' \emph{public processes} (or \emph{behavioral interfaces}~\cite{Weske2012}), i.e., the BPMN tasks and events describing the sending and receiving of messages, as well as the message flow between the participants.
+Collaboration models include the businesses' \emph{public processes} (or \emph{behavioral interfaces}~\cite{Weske2012}), i.e., the BPMN tasks, events and message flows describing the message exchanges between participants.
 While not directly part of the interaction, they can also depict \emph{private processes}, i.e., tasks and control flows that are internally executed before or after sending or receiving a message.
-An example can be seen in Figure \ref{fig:collaboration}.
+An example collaboration model can be seen in Figure \ref{fig:collaboration}.
 
@@
 On the other hand, other nodes can easily verify the signature and come to a consensus regarding the latest state.
-If the same block is signed at the same time, a fork of the blockchain is created, where two versions of the blockchain exist at the same time.
-Consensus is then reached when new blocks are appended, propagating the longest blockchain within the network until it is accepted by all parties.
 
 Blockchain technology is mainly used for cryptocurrencies, most notably Bitcoin~\cite{nakamoto2008bitcoin}.
-In more recent developments however, they are used as a foundation for a number of other decentralized applications.
+In more recent developments however, it is a foundation for a number of other decentralized applications.
 Ethereum~\cite{wood2014ethereum} is a platform that uses a blockchain as the underlying system, but further allows users write and execute code in the form of \emph{smart contracts}.
@@
 Events are publicly visible and can be watched by off-chain applications, allowing external programs to react to blockchain state changes.
-This would otherwise not be possible, ss smart contracts can not communicate with anything outside the blockchain.
+This would otherwise not be possible, as smart contracts can not communicate with anything outside the blockchain.
 
 When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
-Contracts deplete gas for each operation and return excess gas back to the user.
-This ensures that contracts are not running for an unlimited amount of time, avoiding a dead lock of the platform.
-Computations on the blockchain are expensive in order to avoid unnecessary operations, as all operations have to be performed by each node in the network.
-Because of the gas limit and high execution cost, the computational power of smart contracts is limited.
+Contracts deplete gas for each operation.
+This ensures a) that contracts are not running for an unlimited amount of time, avoiding a dead lock of the platform, and b) that computation work is kept small, as all operations have to be performed by each node in the network.
 

### 2018-07-30 paper/paper.tex
Minor stuff
gas costs and rephrasing

@@
 \section{Solution Approach} \label{solutionapproach}
-We propose a system design, that allows choreographies to be executed publicly on the blockchain.
-In the following section, we describe our approach and its architecture.
 
@@
 %TODO add emit event in the diagram
-%TODO rephrasing
-The organizations that did not start the instance creation can detect the new process instance by using their trigger to watch the factory contract.
+All other organizations can detect the created instances by watching the factory contract, using a trigger.
 
@@
 	\centering
-\includegraphics[width=0.9\textwidth]{fig/Armadillo.png}
+\includegraphics[width=\textwidth]{fig/Armadillo.png}
 \caption{Screenshot of the Armadillo web application.}
@@
 \end{table}
-% TODO add exchange rates and $ price? or propmt users to look it up themselves because of changing gas price?
+Because of highly fluctuating exchange rates of USD to ether and ether to gas, the total gas cost varies as well.
+At the time of writing the total cas cost amounted to \$2.50 according to \url{ethgasstation.info}.
 Most of the transactions have proven to come with reasonable gas costs.

### 2018-07-30 paper/paper.tex
Shortening, todos

@@
 The mediator is also responsible for role management, i.e., participants can register users to certain roles with the mediator, who verifies these roles at runtime.
-The architecture features factory contracts, which are responsible for deploying instance contracts for each process instance.
+The architecture features \emph{factory contracts}, which are responsible for deploying instance contracts for each process instance.
 For integrating blockchain and BPM applications, the concept of \emph{triggers} is introduced: Applications that watch events on the blockchain and trigger external API calls.
@@
 We built our implementation based on these concepts.
-However, our solution differs from the solution in~\cite{weber2016untrusted} in the way we realize the execution of collaboration models.
+However, our solution differs from~\cite{weber2016untrusted} in the way we realize the execution of collaboration models.
 As stated before, Weber et al. employ the central mediator contract, managing execution steps and internal state of the collaboration, achieving the orchestration of a business process collaboration.
@@
 We have not made an automated translation our primary goal.
-Instead, we focussed on designing an architecture that allows for the above mentioned choreography implementation.
 However, we believe that an at least semi-automatic translation process can be derived from our results.
 
-Caterpillar~\cite{lopez2017caterpillar} is an open source implementation of a process engine using smart contracts, handling the most common BPMN elements.
-Building on the BPMN-to-Solidity compilation from~\cite{weber2016untrusted}, it integrates translation, deployment and execution of BPMN models in the form of smart contracts directly on the Ethereum Blockchain.
-It also allows a translation of BPMN Models to smart contracts, which can be deployed and executed directly on the Ethereum Blockchain.
-Processes can be started and executed via a user interface, which encapsulates the calls the generated Solidity code in the background.
+Caterpillar~\cite{lopez2017caterpillar} is an open source implementation of a process engine using smart contractsf.
+Building on the BPMN-to-Solidity compilation from~\cite{weber2016untrusted}, it integrates translation, deployment and execution of BPMN models directly on the Ethereum Blockchain.
+Processes can be started and executed via a user interface, which encapsulates the calls to the generated Solidity code in the background.
 
 Our approach is different in that we do not try to use the Ethereum platform as a process engine, but rather use it only for message passing, and integrate it with an off-chain process engine.
-Caterpillar also currently does not support the execution of process interactions.
+Caterpillar also currently does not support the execution of process interactions, which we aim to achieve.
 
@@
 Because we implemented contracts for each participant, we needed to expand the collapsed pool for the \emph{Bulk Buyer}, and add tasks and events for the corresponding public process.
-We added a new lane to the \emph{Manufacturer's} process for demonstration of the role management we implemented.
+Additionally, we added a new lane to the \emph{Manufacturer's} process for demonstration of the role management we implemented.
 The result is depicted in Figure \ref{fig:collaboration}.
 
-When we present the implementation, the tasks that are modeled as BPMN message sends in the collaboration model will instead be modeled as \emph{BPMN service tasks} in the separate processes.
-This decision is based on the notion that in our implementation, all sends are a call to the Ethereum platform, which acts as the external service and takes over the actual messaging.
-This implementation detail is not relevant in the collaboration view, though, where we are concerned with the interactions.
+% When we present the implementation, the tasks that are modeled as BPMN message sends in the collaboration model will instead be modeled as \emph{BPMN service tasks} in the separate processes.
+% This decision is based on the notion that in our implementation, all sends are a call to the Ethereum platform, which acts as the external service and takes over the actual messaging.
+% This implementation detail is not relevant in the collaboration view, though, where we are concerned with the interactions.
 
@@
 
-Every organization provides an interface of their public process in an \emph{instance contract}.
-Additionally, \emph{factory contracts} manage these instance contracts and \emph{access contracts} are used for rights management.
-The contract structure will be described in detail in the following sections.
+Every organization provides an interface to their public process in an \emph{instance contract}.
+Additionally, \emph{factory contracts} manage these instance contracts and \emph{access contracts} are used for user rights management.
+% The contract structure will be described in detail in the following sections.
 We assume that all participating organizations use a process engine to execute their private processes.
-When a throw event is triggered within a process engine, the process engine calls the \emph{throw event function} on an instance contract, which in turn automatically calls the corresponding \emph{catch event function} on the instance contract of the organization responsible for catching the event.
+
+When a throw event is reached within a process engine, the process engine calls the \emph{throw event function} on the company's instance contract, which in turn automatically calls the corresponding \emph{catch event function} on the instance contract of the receiver.
 Thus, all communication between organizations is recorded on the blockchain.
@@
 To realize the system, we use three kinds of smart contracts.
-Firstly, each organization uses one \emph{instance contract} per process instance.
-It represents the public process of the organization for the corresponding process.
-It is called during the process execution when a catch or throw event is reached in the process instance.
-When this happens, it emits an event on the blockchain to document this fact.
+Firstly, each organization deploys one \emph{instance contract} per process instance.
+It represents a public process of the organization and is called during the process execution whenever a catch or throw event is reached in the process instance.
+In the case of catch events, an Ethereum event is logged to the blockchain for documentation.
 
-Secondly, each organization uses one \emph{factory contract} per process.
+Secondly, each organization deploys one \emph{factory contract} per process.
 It is responsible for creating instance contracts and saving a mapping from instance IDs to the corresponding contracts.
 
-Thirdly, each organization uses \emph{access contracts} to manage which users can trigger events on the instance contracts.
+Thirdly, each organization deploys \emph{access contracts} to manage which users can trigger events on the instance contracts.
 Either there is one access contract per process or access contracts are shared over multiple processes depending on the use case.
@@
 \subsection{Per-Company Setup}
+
+%TODO add a step in the diagram where other factory contracts are set
 \begin{figure}
@@
 
-%TODO add a step where other factory contracts are set
-Each organization needs to perform some setup before they can take part in a process execution.
-An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
-Additionally, the user-to-role and and task-to-role mappings have to be updated (via the \emph{giveRights} and \emph{assignRole} functions, respectively), to allow verification of users during the process execution.
-A diagram of this process can be seen in Figure \ref{fig:initialization}.
+Each organization needs to perform certain setup steps before the process execution.
+The factory and access contracts corresponding to the process need to be deployed.
+Additionally, the user-to-role and and task-to-role mappings have to be updated in the access contract (\texttt{giveRights} and \texttt{assignRole}, respectively), to allow verification of users during the process execution.
+Lastly, the addresses of the factory contracts of all communication partners need to be linked in the own factory contract.
+Figure \ref{fig:initialization} shows this setup sequence.
 

### 2018-07-30 paper/paper.tex
Minor stuff

@@
 \subsection{Interaction Setup}
+
+%TODO add emit event in the diagram
 \begin{figure}
@@
 
-In order to create a new process instance, the organization that initiates the instance by triggering the first throw event has to explicitly create an instance contract by calling the factory contract.
-To create an instance contract, the factory contract may need to initialize other instance contracts by calling other factory contracts.
+In order to create a new process instance, the party initiating the choreography has to explicitly create an instance contract by calling the factory contract.
+The factory contract in turn may need to initialize other instance contracts by calling other factory contracts.
 When all partner instance, factory and access contracts are known, the instance contract can be created and its address is returned to the user and an event is emitted to the blockchain.
@@
 
-The recursive initialization ensures that all instance contracts that are part of the process instance will be created by one function call.
-%TODO add emit event in the diagram
+The recursive initialization ensures that all contracts that are part of the process instance will be created by one function call.
 All other organizations can detect the created instances by watching the factory contract, using a trigger.

### 2018-07-30 paper/paper.tex
Remove figure

@@
 \subsection{Contract Structure}
+
 To realize the system, we use three kinds of smart contracts.
@@
 
-%TODO add a step in the diagram where other factory contracts are set
-\begin{figure}
-	\centering
-	\includegraphics[width=0.45\textwidth]{fig/initialization.eps}
-	\caption{A sequence diagram describing the initialization process for an organization.}
-	\label{fig:initialization}
-\end{figure}
-
 Each organization needs to perform certain setup steps before the process execution.
@@
 Lastly, the addresses of the factory contracts of all communication partners need to be linked in the own factory contract.
-Figure \ref{fig:initialization} shows this setup sequence.
 
@@
 	\includegraphics[width=\textwidth]{fig/instance_creation.eps}
-	\caption{A sequence diagram describing the process of creating a new process instance.}
+	\caption{Example sequence diagram describing the creation of a new process instance in our choreography example.}
 	\label{fig:instance_creation}

### 2018-07-30 paper/paper.tex
Move screencast and small changes

@@
 In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
-The implementations can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
-% TODO repo & hbox
+The implementation can be found at \url{https://github.com/p-otto/armadillo}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
 
@@
 Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
-A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/blob/master/presentation/armadillo-screencast.mp4}.
+A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/armadillo/blob/master/presentation/armadillo-screencast.mp4}.
 % TODO repo, hbox etc.

### 2018-07-30 paper/paper.tex
Update repo name and keywords

@@
 
-	\keywords{Business Processes \and BPMN \and Choreographies \and Blockchain \and Ethereum \and Smart Contracts}
+	\keywords{Business Processes \and Choreographies \and Blockchain \and Smart Contracts}
 \end{abstract}
@@
 The recursive initialization ensures that all contracts that are part of the process instance will be created by one function call.
-All other organizations can detect the created instances by watching the factory contract, using a trigger.
+All other organizations can detect the created instances by watching their factory contract, using a trigger.
 
@@
 In the following, we will formally describe our contract implementations.
-The implemented contracts can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/tree/master/armadillo/resources}.
-% TODO repo & hbox
+The specific implemented contracts can be found in our repository in the folder\\\url{https://github.com/p-otto/Armadillo/tree/master/armadillo/resources}.
 
@@
 In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
-The implementation can be found at \url{https://github.com/p-otto/armadillo}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
+The implementation can be found at \url{https://github.com/p-otto/Armadillo}, in the folders \texttt{armadillo} and \texttt{eth\_admin}, respectively.
 
@@
 Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
-A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/armadillo/blob/master/presentation/armadillo-screencast.mp4}.
-% TODO repo, hbox etc.
+A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.
 

### 2018-07-30 paper/paper.tex
Shrink system diagram
Shrink to 15 pages

@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{fig/system_diagram.eps}
+	\includegraphics[width=0.6\textwidth]{fig/system_diagram.pdf}
 	\caption{An architecture diagram showing the interactions within the system.}
@@
 	\centering
-\includegraphics[width=\textwidth]{fig/Armadillo.png}
+\includegraphics[width=0.8\textwidth]{fig/Armadillo.png}
 \caption{Screenshot of the Armadillo web application.}
@@
 Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
-Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
+Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on BPMN \emph{Service Tasks}, which allowed us to use the viewer as a process engine mock.
 A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.
@@
 Having a permanent ledger as the underlying data structure storing messages, faults and misunderstandings can be traced back to their origin and responsibilities are disclosed.
-
 Building on the findings of this paper, improvements regarding runtime and execution costs open up a wide area of possible future work on the topic.

### 2018-07-30 paper/paper.tex
Minor stuff

@@
 \end{table}
-Because of highly fluctuating exchange rates of USD to ether and ether to gas, the total gas cost varies as well.
-At the time of writing the total cas cost amounted to \$2.50 according to \url{ethgasstation.info}.
+
+Because of fluctuating exchange rates of USD to Ether and Ether to gas, the total gas cost varies.
+At the time of writing the total cas cost amounted to \$2.50 according to \url{https://ethgasstation.info}, based on a gas exchange rate of 1 gas = 1 Gwei.
+
 Most of the transactions have proven to come with reasonable gas costs.

### 2018-07-31 paper/paper.tex
Work on solution approach

@@
 
-Before presenting the system, want to give an overview of the functional and non-functional requirements it has to fulfill.
+Before presenting the system, we want to give an overview of the functional and non-functional requirements it has to fulfill.
 
@@
 Firstly, each organization deploys one \emph{instance contract} per process instance.
-It represents a public process of the organization and is called during the process execution whenever a catch or throw event is reached in the process instance.
-In the case of catch events, an Ethereum event is logged to the blockchain for documentation.
+It represents the public process of the organization and is called during process execution whenever a catch or throw event is reached in the execution of a process instance.
+In the case of catch events, an Ethereum event is logged to the blockchain to document the process event.
 
@@
 The factory and access contracts corresponding to the process need to be deployed.
-Additionally, the user-to-role and and task-to-role mappings have to be updated in the access contract (\texttt{giveRights} and \texttt{assignRole}, respectively), to allow verification of users during the process execution.
-Lastly, the addresses of the factory contracts of all communication partners need to be linked in the own factory contract.
+Additionally, the user-to-role and and role-to-permission mappings have to be updated in the access contract (\texttt{giveRights} and \texttt{assignRole}, respectively), to allow verification of users during the process execution.
+Lastly, the addresses of the factory contracts of all communication partners need to be linked in the factory contract.
 
@@
 
-In order to create a new process instance, the party initiating the choreography has to explicitly create an instance contract by calling the factory contract.
-The factory contract in turn may need to initialize other instance contracts by calling other factory contracts.
-When all partner instance, factory and access contracts are known, the instance contract can be created and its address is returned to the user and an event is emitted to the blockchain.
+In order to create a new process instance, the party initiating the choreography has to explicitly call \texttt{createInstance} on their factory contract.
+The factory contract in turn may need to initialize other instance contracts by calling their corresponding factory contracts.
+When all partner instance, factory and access contracts are known, the instance contract can be created, its address is returned to the user and an event is emitted to the blockchain.
 This process is visualized in Figure \ref{fig:instance_creation}.
 
-The recursive initialization ensures that all contracts that are part of the process instance will be created by one function call.
-All other organizations can detect the created instances by watching their factory contract, using a trigger.
+The recursive initialization ensures that all instance contracts that are part of the process instance will be created by one function call.
+The organizations which do not initiate the choreography can detect the newly created instance contracts by watching their factory contracts using a trigger.
 
@@
 If this check is successful, the \emph{catch event function} is called on the partner instance contract of $B$.
-In the instance contract of $B$ there is another authorization against the access contract of $A$.
-This ensures that both sides can be confident, that the throw event was triggered by an authorized person who belongs to organization $A$.
-If this check was also successful, an event is emitted to the blockchain.
-This will be detected by the trigger of $B$ and passed to the process engine.
-Thus, a message was sent from $A$ to $B$ via the blockchain and an audit trail was created.
+In this instance contract there is another authorization against the access contract of $A$.
+This ensures that both sides can be confident that the message was sent by a person who is authorized by organization $A$.
+If both checks are successful, an event is emitted to the blockchain.
+This event will be detected by the trigger of $B$ and passed to their process engine.
+Thus, a message was sent from $A$ to $B$ using the blockchain as a ledger and an audit trail was created.
 An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.

### 2018-07-31 paper/paper.tex
Paper review and update figures

@@
 	We present a smart contract system for inter-process communication, as well as a user interface for connecting business processes and smart contracts.
-	While our solution is not production-ready in terms of transaction costs, it describes a basis for untrusted messaging via the blockchain without a central controlling party.
+	Our solution describes a basis for untrusted messaging via the blockchain without a central controlling party.
 
@@
 The basis for inter-process communication is that all involved parties trust each other.
-Agreements and contracts can help clarifying the requirements and expectations between partners.
+Agreements and contracts can help clarify the requirements and expectations between partners.
 As soon as multiple parties are involved in the handling of a process, though, it becomes difficult to track faults and misunderstandings in the communication.
@@
 Inside this ledger, information is stored in blocks, which are chained together via cryptograhic means.
-Nodes in the network can agree on a public common state of information without trusting each other.
+This allows nodes in the network to agree on a public common state of information without trusting each other.
 Blockchain technology is commonly used to realize virtual currencies, also called cryptocurrencies.
@@
 Such business-to-business collaborations can also be modeled in BPMN.
-Collaboration models include the businesses' \emph{public processes} (or \emph{behavioral interfaces}~\cite{Weske2012}), i.e., the BPMN tasks, events and message flows describing the message exchanges between participants.
-While not directly part of the interaction, they can also depict \emph{private processes}, i.e., tasks and control flows that are internally executed before or after sending or receiving a message.
+Collaboration models include the businesses' \emph{public processes} (or \emph{behavioral interfaces}~\cite{Weske2012}), i.e.
+the BPMN tasks, events and message flows describing the message exchanges between participants.
+While not directly part of the interaction, they can also depict \emph{private processes}, i.e. tasks and control flows that are internally executed before or after sending or receiving a message.
 An example collaboration model can be seen in Figure \ref{fig:collaboration}.
@@
 One option is to treat the collaboration like a local, internal process, employing a \emph{process orchestration}.
-In a process orchestration, the execution is controlled by a central instance.
-Adopting the role of a mediator or manager, this central instance dictates and guides the execution.
+In a process orchestration, the execution is controlled by a central authority.
+Adopting the role of a mediator or manager, this central authority dictates and guides the execution.
 Thus, the execution has a well-defined order of tasks and a clear execution state.
@@
 A blockchain is a distributed ledger that allows users to find a consensus in decentralized applications.
-Information is stored in a linked list of blocks and shared between all participants, i.e., all nodes in a decentralized computer network.
+Information is stored in a linked list of blocks and shared between all participants, i.e. all nodes in a decentralized computer network.
 By only allowing new blocks to be appended to the list, a non-rewritable history is created, that at the same time represents the "truth", the common state all nodes in the network agree on.
 There are multiple approaches of determining who is allowed to append a new block, altering the state.
-The most common one, currently employed for example by Bitcoin~\cite{nakamoto2008bitcoin} and Ethereum~\cite{wood2014ethereum}, is called \emph{proof of work}:
+The most common one, currently employed by Bitcoin~\cite{nakamoto2008bitcoin} and Ethereum~\cite{wood2014ethereum}, is called \emph{proof of work}:
 Each new block has to contain a signature that verifies the block order.
 The signature is created using data from the preceding block and is by design mathematically hard to calculate, but easy to verify.
-On the one hand, this results in a race between so called \emph{mining} nodes who try and calculate such a signature, as the first valid signature verifies the new block's position and stores it's data on the ledger.
+On the one hand, this results in a race between so called \emph{mining} nodes who try and calculate such a signature, as the first valid signature verifies the new blocks position and stores its data on the ledger.
 Mining nodes get rewarded for finding such signatures, creating an incentive for continuous appending of new blocks and keeping the blockchain alive.
@@
 In more recent developments however, it is a foundation for a number of other decentralized applications.
-Ethereum~\cite{wood2014ethereum} is a platform that uses a blockchain as the underlying system, but further allows users write and execute code in the form of \emph{smart contracts}.
+Ethereum~\cite{wood2014ethereum} is a platform that uses a blockchain as the underlying system, and additionally allows users to write and execute code in the form of \emph{smart contracts}.
 Smart contracts are Turing complete code artifacts that can be deployed on the blockchain and are accessible by accounts in the Ethereum platform.
@@
 Events are publicly visible and can be watched by off-chain applications, allowing external programs to react to blockchain state changes.
-This would otherwise not be possible, as smart contracts can not communicate with anything outside the blockchain.
+This would otherwise not be possible, since smart contracts can not communicate with any external APIs.
 
@@
 Contracts deplete gas for each operation.
-This ensures a) that contracts are not running for an unlimited amount of time, avoiding a dead lock of the platform, and b) that computation work is kept small, as all operations have to be performed by each node in the network.
+This ensures a) that contracts are not running for an unlimited amount of time, avoiding a dead lock of the platform, and b) that computations are kept small.
+This is important, because all operations have to be performed by each node in the network.
 
 Smart contracts are executed in the \emph{Ethereum virtual machine (EVM)}.
-As such, they contain byte code that is interpreted by the VM.
+As such, they contain byte code that is interpreted by the EVM.
 When developing smart contracts, there are multiple languages that compile to EVM bytecode, the most prominent one currently being \emph{Solidity}\footnote{\url{https://github.com/ethereum/solidity}}, which we also chose to implement our protoype.
-Xu et al. present patterns and examples for Solidity programming in~\cite{xu2018pattern}, which we used as orientation during development.
+Xu et al. present patterns and examples for Solidity programming in~\cite{xu2018pattern}, which we used as an orientation during development.
 
@@
 Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
-The mediator is also responsible for role management, i.e., participants can register users to certain roles with the mediator, who verifies these roles at runtime.
+The mediator is also responsible for role management, i.e. participants can register users to certain roles with the mediator, who verifies these roles at runtime.
 The architecture features \emph{factory contracts}, which are responsible for deploying instance contracts for each process instance.
@@
 In order to achieve BPMN-to-Solidity compilation,~\cite{weber2016untrusted} also describes translation rules to transform BPMN elements to Solidity code.
-Further work~\cite{banuelos2017optimized} tries to optimize the translation process, in turn reducing Ethereum execution costs by reducing required space and operations.
+Further work~\cite{banuelos2017optimized} optimizes the translation process, in turn reducing Ethereum execution costs by reducing required space and operations.
 
-We have not made an automated translation our primary goal.
-However, we believe that an at least semi-automatic translation process can be derived from our results.
-
-Caterpillar~\cite{lopez2017caterpillar} is an open source implementation of a process engine using smart contractsf.
+Caterpillar~\cite{lopez2017caterpillar} is an open source implementation of a process engine using smart contracts.
 Building on the BPMN-to-Solidity compilation from~\cite{weber2016untrusted}, it integrates translation, deployment and execution of BPMN models directly on the Ethereum Blockchain.
@@
 
-The system's purpose is to facilitate trusted communication and collaboration between untrusting partners.
+The systems purpose is to facilitate trusted communication and collaboration between untrusting partners.
 Therefore, it must be possible to send messages between partners.
 To ensure security and trust in the system, both partners need a way to verify the authenticity of a message.
-Verification is only possible if the system keeps track of users and permissions, i.e., implements a form of role-based access control with a user-to-role and role-to-permission mapping.
+Verification is only possible if the system keeps track of users and permissions, i.e. if it implements a form of role-based access control with a user-to-role and role-to-permission mapping.
 User and permission data has to be accessible at runtime, so that the communicating partners can use it to check the authenticity of messages.
@@
 
-The structure of components for one organization can be seen in Figure \ref{fig:system_diagram}.
-
 \subsection{Contract Structure}
@@
 The factory and access contracts corresponding to the process need to be deployed.
-Additionally, the user-to-role and and role-to-permission mappings have to be updated in the access contract (\texttt{giveRights} and \texttt{assignRole}, respectively), to allow verification of users during the process execution.
+Additionally, the user-to-role and and role-to-permission mappings have to be updated in the access contract to allow verification of users during the process execution.
 Lastly, the addresses of the factory contracts of all communication partners need to be linked in the factory contract.
@@
 
-%TODO add emit event in the diagram
 \begin{figure}
 	\centering
-	\includegraphics[width=\textwidth]{fig/instance_creation.eps}
-	\caption{Example sequence diagram describing the creation of a new process instance in our choreography example.}
+	\includegraphics[width=0.8\textwidth]{fig/instance_creation.pdf}
+	\caption{Example sequence diagram describing the creation of an instance contract of the bulk buyer, cf. Figure \ref{fig:collaboration}.}
 	\label{fig:instance_creation}
@@
 	\centering
-	\includegraphics[width=\textwidth]{fig/event_sending.eps}
-	\caption{A sequence diagram describing the process of sending a message to a collaboration partner.}
+	\includegraphics[width=\textwidth]{fig/event_sending.pdf}
+	\caption{A sequence diagram describing the process of sending a message to a collaboration partner, in this instance the message \emph{request details} that is sent by the special carrier to the supplier in Figure \ref{fig:collaboration}.}
 	\label{fig:event_sending}
@@
 To this end, the factory contract source code needs to contain the definition of the company's instance contract.
-This closely follows the factory contract pattern used in~\cite{weber2016untrusted}, and described as pattern 14 in~\cite{xu2018pattern}.
+This closely follows the factory contract pattern used in~\cite{weber2016untrusted}, which is also described as pattern 14 in~\cite{xu2018pattern}.
 
-In our implementation, a company's factory contract also knows the address of the company's access contract for convenience.
-Additionally, it stores the addresses of created instances, mapped by a \emph{choreography instance ID}, i.e., an ID that is shared between all choreography participants for each instance of the shared choreography.
+In our implementation, a companys factory contract also knows the address of the companys access contract for convenience.
+Additionally, it stores the addresses of created instances, mapped by a \emph{choreography instance ID}, i.e.
+an ID that is shared between all choreography participants for each instance of the shared choreography.
 
@@
 \begin{itemize}
-	\item A \texttt{constructor} where the address of the company's access contract is passed
+	\item A \texttt{constructor} where the address of the companys access contract is passed
 	\item Setter methods for the factory contract addresses of interaction partners
@@
 
-Internally, there are a few implementation details worth mentioning.
-Regarding storage, private fields are necessary holding the factory contract addresses, the access contract address as well as the instance address mapping.
+Regarding storage, private fields are necessary for holding the factory contract addresses, the access contract address as well as the instance address mapping.
 To avoid communication errors at runtime, it should not be possible to call \texttt{createInstance} before all required factory addresses are set.
@@
 Communication between smart contracts happens in the form of function calls.
-To allow the factory and instance contracts to call functions on their interaction partner's contracts, the partner's function interface needs to be known, i.e., it needs to be declared in the factory contract source code.
+To allow the factory and instance contracts to call functions on their interaction partners contracts, the partners function interface needs to be known, i.e.
+it needs to be declared in the factory contract source code.
 %- the access contract (same for every participant)
@@
 The instance contract definition is also part of the factory contract source code.
-The factory contract creates an instance by calling its constructor and passing all for the inter-process communication required addresses.
-Instance contracts provide functions for each sending action, i.e., send tasks or events in the company's process, which can be called by the process engine.
+The factory contract creates an instance by calling its constructor and passing all addresses that are required for the inter-process communication .
+Instance contracts provide functions for each sending action, i.e. send tasks or events in the companys process, which can be called by the process engine.
 For each receiving action (task or event), a function needs to be present that can be called from other instance contracts.
@@
 	\item The addresses of the instance contracts of partners for sending messages
-	\item The address of the company's own access contract, for verifying local function calls
-	\item The address of the company's own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
+	\item The address of the companys own access contract, for verifying local function calls
+	\item The address of the companys own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
 \end{itemize}
 
-A few more implementation details are worth noting:
-Verification is implemented on sender-side and on receiver side.
-Each send function has a guard checking the caller in the company's own access contract.
-Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partner's access contract.
+Verification is implemented on sender side and on receiver side.
+Each send function has a guard checking the caller in the companys own access contract.
+Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partners access contract.
 Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in~\cite{xu2018pattern}.
 
-Having achieved a traceable communication on the blockchain using contract function calls, we still want to access messages in off-chain applications, e.g., triggering process events in a process engine on message receive.
-To this end, smart contracts need to implement events that are emitted to the blockchain whenever a receive function is executed.
-Blockchain events can then be watched, and reacted upon, by off-chain components.
+Having achieved a traceable communication on the blockchain using contract function calls, we still want to access messages in off-chain applications, e.g.
+triggering process events in a process engine on message receive.
+To this end, smart contracts need to implement blockchain events that are emitted to the blockchain ledger whenever a receive function is executed.
+These events can then be watched, and reacted upon, by off-chain components.
 
-In our current implementation, the end of a process instance is marked by the instance contract selfdestructing.
+In our current implementation, the end of a process instance is marked by the instance contract self-destructing.
 At the end of the execution of the last send or receive function in the process, the solidity builtin \texttt{selfdestruct} is called.
@@
 
-Each company deploys an access contract that holds information about the roles and permissions of the company's employees.
+Each company deploys an access contract that holds information about the roles and permissions of the companys employees.
 Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from~\cite{xu2018pattern}.
@@
 Given this interface, there are multiple possible implementation approaches for access contracts.
-As it was our main focus to develop a running prototype, and not to provide an optimized, production-ready system, we decided on a simple mapping-based implementation:
+We decided on a simple mapping-based implementation:
 \begin{lstlisting}[
@@
 The first mapping stores the tasks that can be executed by a specific role (cf. pools and lanes, and their contained tasks, in BPMN diagrams).
-The second mapping assigns each role an index in the access bitmask, i.e., if the bit at the given index is set, the user holds the corresponding role.
+The second mapping assigns each role an index in the access bitmask, i.e. if the bit at the given index is set, the user holds the corresponding role.
 The third mapping assigns such an access bitmask to each user.
-
-Storing large amounts data on the blockchain is expensive by design.
-As the mappings grow in size with each user, role and task that is part of some process in the company, our implementation is probably not suited for real-world application.
-Finding optimized, less costly (both in computation cost and storage cost) approaches is part of future work.
-One other approach we thought of is based on pattern 5 of~\cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify one's role.
 
@@
 
-In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
+In the following, we will briefly present the tools we implemented to evaluate our approach.
 The implementation can be found at \url{https://github.com/p-otto/Armadillo}, in the folders \texttt{armadillo} and \texttt{eth\_admin}, respectively.
@@
 	\centering
-\includegraphics[width=0.8\textwidth]{fig/Armadillo.png}
+\includegraphics[width=0.9\textwidth]{fig/Armadillo.png}
 \caption{Screenshot of the Armadillo web application.}
@@
 With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
-Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
-Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on BPMN \emph{Service Tasks}, which allowed us to use the viewer as a process engine mock.
-A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.
+Armadillo also implements uploading and rendering BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
+Building upon the BPMN viewer provided in the toolkit, we implemented handling of user clicks on BPMN \emph{Service Tasks}, which allowed us to use the viewer as a placeholder for a process engine .
+A screencast of the full choreography can be found in our repository: \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.
 
@@
 We developed a small command line application for managing users and roles via the access contract.
-The application is written in JavaScript in the node.js framework\footnote{\url{https://nodejs.org/}}.
-Internally, calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
+The application is written in JavaScript using the node.js framework\footnote{\url{https://nodejs.org/}}.
+Internally, it calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
 We decided to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
@@
 First, computation and data storage on the blockchain needs to be paid for in \emph{transaction fees}.
-In Ethereum, the unit \emph{gas} was introduced as a way of having consistent fee pricing in spite of fluctuating Ether prices.
+In Ethereum, transaction fees are paid for in \emph{gas}.
+It is a unit that is used up by any instruction a contract executes.
+Users can set gas prices for transactions, which affect how likely it is that the transaction gets executed by miners.
+Therefore, higher gas prices lead to faster execution of transactions.
 
-We measured the gas used for each transaction that is executed by the Armadillo tool, and we summed up the gas usage for the different kinds of contracts in the companies in Table \ref{gasusage}:
+We measured the gas usage for each transaction that is executed by the Armadillo tool, and we summed it up for the different kinds of contracts in the companies in Table \ref{gasusage}:
 
@@
 
-Second, security is one of the main reasons to opt for blockchain systems.
+Security is one of the main reasons to use blockchain systems.
 In our case, we put effort into making the message exchange secure by adding multiple steps of access verification using the access contracts.
@@
 
-During evaluation, we saw that the instantiation costs are very high, have a potential to hit the gas limit in larger choreographies and also have to be paid by the initiator.
+During evaluation, we saw that the instantiation costs are very high, have a potential to hit the gas limit in larger choreographies and also have to be paid fully by the initiator.
 These problems need to be addressed before our solution is feasible for production use.
+
 Further research thus could be invested into a more decentralized instantiation, where each participant pays for its own instance contract creation.
-One apporach worth considering is to have the intiator emit a specific instance creation event that each other participant would listen to.
-The process engine could then react to such an event with the help of a trigger, and call the \texttt{createInstance} method.
-Then the other factory would have to be notified that the instantiation was successful.
+We propose to have the initiator emit a specific instance creation event that all other participants would listen to.
+The process engine then reacts to such an event with the help of a trigger, and calls the \texttt{createInstance} method.
+Then the other factory is notified that the instantiation was successful.
 
@@
 
-As stated earlier, there probably are better ways of implementing role-based access control in a smart contract.
-We decided for a simple mapping-based approach, which requires large amounts of memory.
-Finding approaches that are more suited for blockchain architectures is one direction in which further research could go.
+To implement access right management, we decided for a simple mapping-based approach, which requires large amounts of memory.
+Storing large amounts data on the blockchain is expensive by design.
+As the mappings grow in size with each user, role and task, costs rise.
+Finding optimized and cheaper (both in computation cost and storage cost) approaches is part of future work.
+
+An alternative approach for access control can be implemented based on pattern 5 of~\cite{xu2018pattern} - depicting real world permissions as tokens, and "paying" with these tokens on function call to verify ones role.
 
@@
 Having reached the final iteration, we realized that the contracts share common patterns.
-Most of the implementation could probably be generated, i.e., from a choreography diagram (or at least from the participant's public processes).
-The next step would be to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments, e.g., depending on whether the participant is the initiator or not.
-Given such a template, one could work on a contract generation tool that takes a diagram as input and produces factory contract code.
+
+Most of the implementation can be generated, e.g. from a choreography diagram (or at least from the participants public processes).
+The next step is to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments.
+Given such a template, one can work on a contract generation tool that takes a diagram as input and produces factory contract code.
 A possible implementation could use a rule-based approach for translating the choreography model, similar to~\cite{lopez2017caterpillar}.
@@
 In related work~\cite{lopez2017caterpillar}, process logic was executed on the blockchain.
-As we decided for a hybrid approach, using a process engine for execution and the Ethereum blockchain for traceable message passing, we implemented a mock process engine in our application.
-Now, it certainly makes sense to integrate the system with a productive process engine implementation, e.g., the Camunda BPMN Workflow Engine\footnote{\url{https://camunda.com/products/bpmn-engine}} for further evaluation.
+As we decided for a hybrid approach, using a process engine for execution and the Ethereum blockchain for traceable message passing, we implemented a placeholder process engine in our application.
+
+The next step is to integrate the system with a productive process engine implementation, e.g.
+the Camunda BPMN Workflow Engine\footnote{\url{https://camunda.com/products/bpmn-engine}}, for further evaluation.
 
@@
 
+Currently, blockchain technology is most widely used to handle monetary transactions.
+Instead of shifting assets between partners, however, we are using the blockchain to shift \emph{responsibilities}.
 In this paper, we presented a system architecture and prototypical implementation for connecting process execution with blockchain technology.
@@
 
-Currently, blockchain technology is most widely used to handle monetary transactions.
-Instead of shifting assets between partners, however, we are using the blockchain to shift \emph{responsibilities}.
-Given the similar nature of the two, we speculate that this topic is of future relevance.
 %

### 2018-07-31 paper/paper.tex
Fix possesive

@@
 
-In our implementation, a companys factory contract also knows the address of the companys access contract for convenience.
+In our implementation, a company's factory contract also knows the address of the company's access contract for convenience.
 Additionally, it stores the addresses of created instances, mapped by a \emph{choreography instance ID}, i.e.
@@
 \begin{itemize}
-	\item A \texttt{constructor} where the address of the companys access contract is passed
+	\item A \texttt{constructor} where the address of the company's access contract is passed
 	\item Setter methods for the factory contract addresses of interaction partners
@@
 Communication between smart contracts happens in the form of function calls.
-To allow the factory and instance contracts to call functions on their interaction partners contracts, the partners function interface needs to be known, i.e.
+To allow the factory and instance contracts to call functions on their interaction partner's contracts, the partner's function interface needs to be known, i.e.
 it needs to be declared in the factory contract source code.
@@
 The factory contract creates an instance by calling its constructor and passing all addresses that are required for the inter-process communication .
-Instance contracts provide functions for each sending action, i.e. send tasks or events in the companys process, which can be called by the process engine.
+Instance contracts provide functions for each sending action, i.e. send tasks or events in the company's process, which can be called by the process engine.
 For each receiving action (task or event), a function needs to be present that can be called from other instance contracts.
@@
 	\item The addresses of the instance contracts of partners for sending messages
-	\item The address of the companys own access contract, for verifying local function calls
-	\item The address of the companys own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
+	\item The address of the company's own access contract, for verifying local function calls
+	\item The address of the company's own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
 \end{itemize}
@@
 Verification is implemented on sender side and on receiver side.
-Each send function has a guard checking the caller in the companys own access contract.
-Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partners access contract.
+Each send function has a guard checking the caller in the company's own access contract.
+Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partner's access contract.
 Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in~\cite{xu2018pattern}.
@@
 
-Each company deploys an access contract that holds information about the roles and permissions of the companys employees.
+Each company deploys an access contract that holds information about the roles and permissions of the company's employees.
 Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from~\cite{xu2018pattern}.
@@
 
-Most of the implementation can be generated, e.g. from a choreography diagram (or at least from the participants public processes).
+Most of the implementation can be generated, e.g. from a choreography diagram (or at least from the participant's public processes).
 The next step is to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments.

### 2018-07-31 paper/paper.tex
More review

@@
 	Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
-	Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
+	Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central authority.
 	As a result, it is possible to form consensus in the communication between otherwise untrusting parties.
@@
 % What is Blockchain?
-With the help of the emerging Blockchain technology, these problems can be resolved.
-A Blockchain network is a network of computation nodes sharing a decentralized information storage structure, a \emph{ledger}.
+With the help of the emerging blockchain technology, these problems can be resolved.
+A blockchain network is a network of computation nodes sharing a decentralized information storage structure, a \emph{ledger}.
 Inside this ledger, information is stored in blocks, which are chained together via cryptograhic means.
@@
 Blockchain technology is commonly used to realize virtual currencies, also called cryptocurrencies.
-Ethereum~\cite{wood2014ethereum} is one implementation of the Blockchain concept which also realizes a feature called smart contracts.
-Smart contracts are small programs with limited processing power that are executed by the nodes in the Blockchain network.
+Ethereum~\cite{wood2014ethereum} is one implementation of the blockchain concept which also realizes a feature called smart contracts.
+Smart contracts are small programs with limited processing power that are executed by the nodes in the blockchain network.
 
@@
 % What approaches exist currently (Caterpillar~\cite{lopez2017caterpillar}, Untrusted paper~\cite{weber2016untrusted})
-Approaches exist that aim to bring BPM functionality to the Ethereum Blockchain utilizing smart contracts.
-Weber et al.~\cite{weber2016untrusted} realize process orchestrations on the Blockchain using a smart contract as the mediator for messages and execution state.
+Approaches exist that aim to bring BPM functionality to the Ethereum blockchain utilizing smart contracts.
+Weber et al.~\cite{weber2016untrusted} realize process orchestrations on the blockchain using a smart contract as the mediator for messages and execution state.
 % What is our general Idea?
 We expand on the work of Weber et al. and implement process choreographies, where instead of one central mediator, each party provides their own smart contracts.
-Communication then happens directly between the partner's contracts instead of passing through a central instance.
+Communication then happens directly between the partners' contracts instead of passing through a central instance.
 
@@
 In Section \ref{solutionapproach} we will present the solution requirements and concepts.
-Section \ref{implementation} describes our contract and tool implementations.
+Section \ref{implementation} describes our smart contract and tool implementations.
 In Section \ref{evaluation} we discuss our solution.
@@
 \subsection{Prior Work on Business Processes on the Blockchain}
-In~\cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
+In~\cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain is presented.
 Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
@@
 Caterpillar~\cite{lopez2017caterpillar} is an open source implementation of a process engine using smart contracts.
-Building on the BPMN-to-Solidity compilation from~\cite{weber2016untrusted}, it integrates translation, deployment and execution of BPMN models directly on the Ethereum Blockchain.
+Building on the BPMN-to-Solidity compilation from~\cite{weber2016untrusted}, it integrates translation, deployment and execution of BPMN models directly on the Ethereum blockchain.
 Processes can be started and executed via a user interface, which encapsulates the calls to the generated Solidity code in the background.
